---
title: "Seattle dataset results"
output: 
  #github_document
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: journal
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jtools)
library(readr)
library(dplyr)

library(jtools)
library(caret)
library(MASS)
library(tibble)
library(broom)

library(DMwR)  ## for unscale

options(scipen=10) # avoid scientific notation in plots

```


```{r}
variableImportance <- function(m) {
  vi.int <- varImp(m) %>% 
       mutate(Variable=row.names(.)) %>%
       #mutate(Overall=round(Overall,2)) %>%
       mutate(Percentage = round(Overall*100/sum(Overall), 2)) %>%
       arrange(-Percentage)
  return(vi.int)
}

coefTable <- function(m) {
  intCoeff <- as.data.frame(summary(m)$coefficients) %>%
       mutate(Variable = rownames(.)) %>%
       mutate(pVal = round(`Pr(>|t|)`, 4)) %>%
       arrange(pVal) %>%
       mutate(Significance = 
                case_when(pVal <= 0.001 ~ "0.001", 
                          pVal > 0.001 & pVal <= 0.01 ~ "0.01",
                          pVal > 0.01  & pVal <= 0.05 ~ "0.05",
                          pVal > 0.05  & pVal <= 0.1  ~ "0.1",
                          pVal > 0.1   & pVal <= 0.2  ~  "0.2"))
  return(intCoeff)
}

filterCoefTable <- function(coefTab) {
  coefTab1 = coefTab %>% 
    #filter(!is.na(Significance)) %>%
    filter(Significance <= 0.1) %>%
    dplyr::select(Variable,pVal,Significance)
  return(coefTab1)
}
```


```{r}
# Loading all non-interacation models
lm1a = readRDS("SiteEnergyUseLog_Scale_lmFitSW.RDS")
lm1b = readRDS("SiteEnergyUseLog_NoScale_lmFitSW.RDS")
lm1c = readRDS("SiteEnergyUse_NoScale_lmFitSW.RDS")

lm1a.coef = coefTable(lm1a)
lm1b.coef = coefTable(lm1b)
lm1c.coef = coefTable(lm1c)

lm1a.coef1 = filterCoefTable(lm1a.coef)
lm1b.coef1 = filterCoefTable(lm1b.coef)
lm1c.coef1 = filterCoefTable(lm1c.coef)

lm1a.vi = variableImportance(lm1a)
lm1b.vi = variableImportance(lm1b)
lm1c.vi = variableImportance(lm1c)

######## using source eui
lm2a = readRDS("SourceEUILog_Scale_lmFitSW.RDS")
lm2b = readRDS("SourceEUILog_NoScale_lmFitSW.RDS")
lm2c = readRDS("SourceEUI_NoScale_lmFitSW.RDS")

lm2a.coef = coefTable(lm2a)
lm2b.coef = coefTable(lm2b)
lm2c.coef = coefTable(lm2c)

lm2a.coef1 = filterCoefTable(lm2a.coef)
lm2b.coef1 = filterCoefTable(lm2b.coef)
lm2c.coef1 = filterCoefTable(lm2c.coef)

lm2a.vi = variableImportance(lm2a)
lm2b.vi = variableImportance(lm2b)
lm2c.vi = variableImportance(lm2c)
# options(max.print=99)
# coef = m$coefficients[!is.na(m$coefficients) ]
# 
# ss = summary(m)
# View(ss$coefficients)
# print(nrow(ss$coefficients))
#summ(m)
```



```{r}
# Loading all interacation models
m1a = readRDS("SiteEnergyUseLog_Scale_IntlmFit.RDS")
m1b = readRDS("SiteEnergyUseLog_NoScale_IntlmFit.RDS")
m1c = readRDS("SiteEnergyUse_NoScale_IntlmFit.RDS")

m1a.coef = coefTable(m1a)
m1b.coef = coefTable(m1b)
m1c.coef = coefTable(m1c)

m1a.coef1 = filterCoefTable(m1a.coef)
m1b.coef1 = filterCoefTable(m1b.coef)
m1c.coef1 = filterCoefTable(m1c.coef)

m1a.vi = variableImportance(m1a)
m1b.vi = variableImportance(m1b)
m1c.vi = variableImportance(m1c)

######## using source eui
m2a = readRDS("SourceEUILog_Scale_IntlmFit.RDS")
m2b = readRDS("SourceEUILog_NoScale_IntlmFit.RDS")
m2c = readRDS("SourceEUI_NoScale_IntlmFit.RDS")

m2a.coef = coefTable(m2a)
m2b.coef = coefTable(m2b)
m2c.coef = coefTable(m2c)

m2a.coef1 = filterCoefTable(m2a.coef)
m2b.coef1 = filterCoefTable(m2b.coef)
m2c.coef1 = filterCoefTable(m2c.coef)

m2a.vi = variableImportance(m2a)
m2b.vi = variableImportance(m2b)
m2c.vi = variableImportance(m2c)
# options(max.print=99)
# coef = m$coefficients[!is.na(m$coefficients) ]
# 
# ss = summary(m)
# View(ss$coefficients)
# print(nrow(ss$coefficients))
#summ(m)
```

# Comparision of all models WITHOUT interactions
```{r}
li = list( 
  "log(SiteEnergyUse) - mean centering" = lm1a,
  "log(SiteEnergyUse) - No mean centering" = lm1b, 
  "SiteEnergyUse - No mean centering" = lm1c,
  
  "log(SourceEUI) - mean centering" = lm2a,
  "log(SourceEUI) - No mean centering" = lm2b, 
  "SourceEUI - No mean centering" = lm2c
)

all.coef = bind_rows(
  lapply(names(li), function(x){
    #print(paste("processing ", x))
    m = li[[x]]
    gl = add_column(round(glance(m),3), .before = 1, model = x)
    coef = coefTable(m)
    coef1 = filterCoefTable(coef)
    df = as.data.frame.matrix(t(table(coef1$Significance)))
    
    coef1 = subset(coef1, Variable != "(Intercept)")
    df["Variables"] = coef1$Variable[1]
    cbind(gl,df)
}))

all1 = all.coef[, c(1:3, 13:17)]
knitr::kable(all1)
```


# Comparision of all models WITH interactions
```{r}
# ###########
# ########### OLD CODE
# #########
# #make a table of significance for all experiments
# li = list(m1a.coef1, m1b.coef1, m1c.coef1, 
#           m2a.coef1, m2b.coef1, m2c.coef1)
# 
# all.si = bind_rows(
#   lapply(li, function(x){
#     df = as.data.frame.matrix(t(table(x$Significance)))
#     df["Variables"] = x$Variable[1]
#     df
# }))
# 
# all = add_column(round(glance(m1a),3), .before = 1, 
#                  model = "log(SiteEnergyUse) - mean centering")
# all = bind_rows(all, add_column(round(glance(m1b),3), .before = 1,
#                                 model = "log(SiteEnergyUse) - No mean centering"))
# all = bind_rows(all, add_column(round(glance(m1c),3), .before = 1, 
#                                 model = "SiteEnergyUse - No mean centering"))
# 
# all = bind_rows(all, add_column(round(glance(m2a),3), .before = 1, 
#                                 model = "log(SourceEUI) - mean centering"))
# all = bind_rows(all, add_column(round(glance(m2b),3), .before = 1, 
#                                 model = "log(SourceEUI) - No mean centering"))
# all = bind_rows(all, add_column(round(glance(m2c),3), .before = 1, 
#                                 model = "SourceEUI - No mean centering"))
# 
# all = bind_cols(all, all.si)
# 
# all1 = all[, c(1:3, 13:17)]
# 
# #so=summ(fit.model)
# #knitr::kable(glance.summ.lm(so))
# knitr::kable(all1)

```

```{r}
li = list( 
  "log(SiteEnergyUse) - mean centering" = m1a,
  "log(SiteEnergyUse) - No mean centering" = m1b, 
  "SiteEnergyUse - No mean centering" = m1c,
  
  "log(SourceEUI) - mean centering" = m2a,
  "log(SourceEUI) - No mean centering" = m2b, 
  "SourceEUI - No mean centering" = m2c
)

all.coef = bind_rows(
  lapply(names(li), function(x){
    #print(paste("processing ", x))
    m = li[[x]]
    gl = add_column(round(glance(m),3), .before = 1, model = x)
    coef = coefTable(m)
    coef1 = filterCoefTable(coef)
    df = as.data.frame.matrix(t(table(coef1$Significance)))
    df["Variables"] = coef1$Variable[1]
    cbind(gl,df)
}))

all1 = all.coef[, c(1:3, 13:17)]
knitr::kable(all1)
```

# Experimental results using SiteEnergyUse and interactions

## 1A. Using log(SiteEnergyUse) and scaling all variables
```{r}
knitr::kable(m1a.coef1)
```


## 1B. Using log(SiteEnergyUse) and but NOT scaling all variables
```{r}
knitr::kable(m1b.coef1)
```


## 1C. Using SiteEnergyUse and NOT scaling all variables
```{r}
knitr::kable(m1c.coef1)
```

```{r}
library(DMwR)  ## for unscale
unscale_data <- function(df) {
  for(col in names(df)) {
    if( is.numeric(df[, col]) ){
      # https://stackoverflow.com/questions/10287545/backtransform-scale-for-plotting
      # https://rdrr.io/cran/DMwR/man/unscale.html
      #df[, col] = scale(df[, col], center = T, scale = T)
      df[, col] = unscale(df[, col], df[, col])
    }
  }
  return (df)
}

```

## Ranking using EER calculation - using model 1A. log(SiteEnergyUse) and scaling all variables
```{r}
step.model = m1a
dat0 = step.model$model
pre0 = predict(step.model, dat0)
pre = unscale(pre0, dat0$SiteEnergyUseLog)

dat = unscale_data(dat0)

eer = dat$SiteEnergyUseLog / pre
dat["eer"] = round(eer,2)

eer_sorted = sort(eer)
     #plot(eer_sorted, xlab = "Building Id", ylab = "Energy Efficiency Ratio")
     
     # Plot cumaltive percentage for energy efficiency ratio
eer_cs = cumsum(eer_sorted)
eer_pr = cumsum(eer_sorted) / sum(eer_sorted)

summary(eer_sorted)
hist(eer_sorted)
#plot(eer_sorted)

plot(eer_sorted,eer_pr, main = "Cumalativer percentile of EER",
     cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5,
     #cex.lab=2.0, cex.axis=2.0, cex.main=2.0, cex.sub=2.0,
     xlab = "Energy Efficiency Ratio", 
     ylab = "Cumalative percentile")


abline(h = 0.8, col = "red", lwd = 2)
abline(v = 1.6, col = "blue", lwd = 2)

```

## Ranking using EER and clustering - using model 1A. log(SiteEnergyUse) and scaling all variables
```{r}
library(Ckmeans.1d.dp)

k = 5
result <- Ckmeans.1d.dp(eer_sorted, k, y=eer_sorted)
plot(result)

result <- Ckmeans.1d.dp(eer_sorted, y=eer_sorted)
plot(result)

k = 5
result <- Ckmedian.1d.dp(eer_sorted, k)
plot(result)

result <- Ckmedian.1d.dp(eer_sorted)
plot(result)

```



# Experimental results using SourceEUI and interactions


## 2A. Using log(SiteEnergyUse) and scaling all variables
```{r}
knitr::kable(m2a.coef1)
```


## 2B. Using log(SiteEnergyUse) and but NOT scaling all variables
```{r}
knitr::kable(m2b.coef1)
```


## 2C. Using SiteEnergyUse and NOT scaling all variables
```{r}
knitr::kable(m2c.coef1)
```


## Ranking using EER calculation - using model 1A. log(SourceEUI) and scaling all variables
```{r}
step.model = m2a
dat0 = step.model$model
pre0 = predict(step.model, dat0)
pre = unscale(pre0, dat0$SourceEUILog)

dat = unscale_data(dat0)

eer = dat$SourceEUILog / pre
dat["eer"] = round(eer,2)

eer_sorted = sort(eer)
     #plot(eer_sorted, xlab = "Building Id", ylab = "Energy Efficiency Ratio")
     
     # Plot cumaltive percentage for energy efficiency ratio
eer_cs = cumsum(eer_sorted)
eer_pr = cumsum(eer_sorted) / sum(eer_sorted)

summary(eer_sorted)
hist(eer_sorted)
#plot(eer_sorted)

plot(eer_sorted,eer_pr, main = "Cumalativer percentile of EER",
     cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5,
     #cex.lab=2.0, cex.axis=2.0, cex.main=2.0, cex.sub=2.0,
     xlab = "Energy Efficiency Ratio", 
     ylab = "Cumalative percentile")


abline(h = 0.8, col = "red", lwd = 2)
abline(v = 1.6, col = "blue", lwd = 2)

```

## Ranking using EER and clustering - using model 1A. log(SourceEUI) and scaling all variables
```{r}
library(Ckmeans.1d.dp)

k = 5
result <- Ckmeans.1d.dp(eer_sorted, k, y=eer_sorted)
plot(result)

result <- Ckmeans.1d.dp(eer_sorted, y=eer_sorted)
plot(result)

k = 5
result <- Ckmedian.1d.dp(eer_sorted, k)
plot(result)

result <- Ckmedian.1d.dp(eer_sorted)
plot(result)

```