---
title: "CBECS Multifamily Houses - Data filteration"
author: "Pandarasamy Arjunan"
date: "3 June 2019"
output: 
  github_document:
    toc: true
#  html_document:
#    code_folding: "hide"
#    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load dataset
```{r message=FALSE, warning=FALSE}
library(dplyr)
library(readr)

save_dir1 = './data/filtered/'
dir.create(save_dir1, showWarnings = F)

save_dir2 = './data/features/'
dir.create(save_dir2, showWarnings = F)

```

The reference data used to establish the peer building population in the United States is Fannie Mae’s Multifamily Energy and Water Market Research Survey.

```{r, warning=FALSE}
multifamily = read_csv("data/FannieMae/mewmr-survey-database_data.csv")

## remove all special chars 
cols = names(multifamily)
cols <- gsub("[^0-9A-Za-z// ]","" , cols ,ignore.case = TRUE)
cols = gsub("  ", "", cols, fixed = TRUE)
names(multifamily) = make.names(cols, unique = T)

cols = c( "Total.gross.floor.area",
           "Total.number.of.units",
           "Unit.Density",
           "Bedrooms.Unit",
           "Number.of.BRs",
           "CDD", 
           "HDD",
           "Building.Type.Property.Level",
           "Total.SOURCE.kBtu",
           "Total.SITE.kBtu",
           "Source.EUI.using.Total.gross.floor.area",
           "Site.EUIusing.Total.gross.floor.area",
           "Survey.Weights.for.ENERGY.STAR.score.analysis")


```


## Apply filters

As per Energy Star's technical document [ENERGY STAR Score for Multifamily Housing in the United States](https://www.energystar.gov/buildings/tools-and-resources/energy_star_score_multifamily_housing_united_states), following filters are applied to define the peer group and to remove any outliers.

After applying each filter, the number of remaining buildings in the dataset (_Number Remaining: X_) and any difference (_Difference: X_) in count from the original Energy Star's technical documentation is also given. 


#. **Must have complete data for whole-property energy use and operating characteristics**
<br/>EPA Program Filter – Complete data is necessary for analysis.
<br/>Number Remaining: 357
<br/>Difference: +7.
    ```{r}
m0a = multifamily %>% 
  filter(Energy.Space.Served == "Whole property") %>%
  filter(X12.months.of.energy.data.provided == "Y") %>%
  #filter(Survey.Weights.for.ENERGY.STAR.score.analysis > 0) %>% 
  filter(Total.gross.floor.area > 0) %>% 
  filter(Total.number.of.units > 0) %>%
  filter(Unit.Density > 0) %>% 
  filter(Number.of.BRs > 0) %>%
  filter(Bedrooms.Unit > 0) %>%
  filter(CDD > 0) %>% 
  filter(HDD > 0) %>% 
  filter(Building.Type.Property.Level != "Not Provided")

m0b = m0a %>% 
  filter(Total.SOURCE.kBtu > 0) %>%
  filter(Total.SITE.kBtu > 0) %>%
  filter(Source.EUI.using.Total.gross.floor.area > 0)
  
m0c = m0b %>% filter( Total.number.of.units > 0 &
                        Unit.Density > 0 & 
                        Bedrooms.Unit > 0 & 
                        CDD > 0 & 
                        HDD > 0 )

    ```


#. **Must have at least 20 units**
<br/>Analytical filter – Analysis could not model behavior for buildings with fewer than 20 units, due to limited data.
<br/>Number Remaining: 351.
<br/>Difference: +9
    ```{r}
m1 = m0c %>% filter(Total.number.of.units >= 20)
    ```


#. **Source EUI must be less than 290 kBtu/ft2**
<br/>Analytical filter – Values determined to be data entry errors or statistical outliers.
<br/>Number Remaining: 347.
<br/>Difference: +14.
    ```{r}
m2 = m1 %>% filter(Source.EUI.using.Total.gross.floor.area > 0 & 
                     Source.EUI.using.Total.gross.floor.area < 290)
    ```


#. **Gross Floor area must be no more than 2,000,000 ft2**
<br/>Analytical filter – Values determined to be data entry errors or statistical outliers.
<br/>Number Remaining: 346
<br/>Difference: +14.
    ```{r}
m3 = m2 %>% filter(Total.gross.floor.area <= 2000000)
    ```


#. **Unit density must be less than 2.75 units per 1,000 square feet**
<br/>Analytical filter – Values determined to be data entry errors or statistical outliers.
<br/>Number Remaining: 338.
<br/>Difference: +11.
    ```{r}
m4 = m3 %>% filter(Unit.Density < 2.75)
    ```

#. **Bedroom Density must be more than 0.5 and less than 3.5 bedrooms per 1,000 square feet**
<br/>Analytical filter – Values determined to be data entry errors or statistical outliers.
<br/>Number Remaining: 336
<br/>Difference: +12.
    ```{r}
m5 = m4 %>% filter(Bedrooms.Unit > 0.5 & Bedrooms.Unit < 3.5)
    ```

#. **Other filters - Survey weights should be positive**
<br/>Number Remaining: 321
<br/>Difference: -1.
    ```{r}
m6 = m5 %>% filter(Unit.Density > 0 & 
                     Bedrooms.Unit > 0 & 
                     CDD > 0 & 
                     HDD > 0 & 
                     Survey.Weights.for.ENERGY.STAR.score.analysis > 0)
    ```

**Save the filtered dataset**
```{r}
m7 = m6[, cols]
write.csv(m7, paste0(save_dir1, "multifamily.csv"), row.names = F)
```


## Prepare features

The final regression equation includes the following variables: 
 
 - Number of Units per 1,000 square feet
 - Number of Bedrooms per Unit
 - Total Heating Degree Days
 - Total Cooling Degree Days
 - Low-Rise building (yes/no)

```{r}
save_dir1 = './data/filtered/'
save_dir2 = './data/features/'

multifamily = read.csv(paste0(save_dir1, "multifamily.csv"))

data = multifamily %>% 
  mutate(IsLowRise = 
           ifelse(Building.Type.Property.Level == "Low-rise", "Yes", "No")) 

ivars = c( "Total.gross.floor.area",
           "Unit.Density",
           "Bedrooms.Unit",
           "CDD", 
           "HDD", 
           "IsLowRise")

dvars = c("Total.SITE.kBtu",
          "Total.SOURCE.kBtu",
          "Site.EUIusing.Total.gross.floor.area",
          "Source.EUI.using.Total.gross.floor.area",
          "Survey.Weights.for.ENERGY.STAR.score.analysis")

features = data %>% 
  dplyr::select(c(ivars, dvars)) %>%
  dplyr::rename(SQFT = Total.gross.floor.area) %>%
  dplyr::rename(SITE_ENERGY = Total.SITE.kBtu) %>%
  dplyr::rename(SOURCE_ENERGY = Total.SOURCE.kBtu) %>%
  dplyr::rename(SITE_EUI = Site.EUIusing.Total.gross.floor.area) %>%
  dplyr::rename(SOURCE_EUI = Source.EUI.using.Total.gross.floor.area) %>%
  dplyr::rename(FINALWT = Survey.Weights.for.ENERGY.STAR.score.analysis) %>%
  dplyr::select(-c(SQFT, SITE_EUI, SITE_ENERGY))

#summary(features)
features = features %>% na.omit()
write.csv(features, paste0(save_dir2, "multifamily.csv"), row.names = F)

```

## Descriptive statistics 

```{r include=FALSE}
library(knitr)
opts_chunk$set(results = 'asis',      
              comment = NA, 
              prompt = FALSE, 
              cache = FALSE)

library(summarytools)
st_options(plain.ascii = FALSE,       
            style = "rmarkdown",      
            footnote = NA,            
            subtitle.emphasis = FALSE)                                    
st_css()                              
```


```{r}
features1 = features
features1 = features1 %>% dplyr::select(-one_of('SOURCE_ENERGY', 'FINALWT'))

summarytools::descr(features1, stats = "common", 
                    transpose = TRUE, 
                    headings = FALSE)
```


```{r}
dfSummary(features1, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE)
```


**Extract R code from Rmd document**
```{r}
#knitr::purl("multifamily.Rmd", output = "multifamily.R", documentation = 2)
```

