---
title: "Benchmarking Multifamily Houses"
author: "Pandarasamy Arjunan"
date: "3 June 2019"
output: 
  github_document:
    toc: true
#  html_document:
#    code_folding: "hide"
#    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(readr)
library(Metrics)
library(caret)
library(xgboost)
library(ggplot2)
library(reshape2)
library(ggpubr)
```


## Load dataset
```{r message=FALSE, warning=FALSE}
building_type = "multifamily"

filtered_dir = './data/cbecs/filtered/'
dir.create(filtered_dir, recursive = T, showWarnings = F)

features_dir = './data/cbecs/features/'
dir.create(features_dir, recursive = T, showWarnings = F)

results_dir = './results/cbecs/'
dir.create(results_dir, recursive = T, showWarnings = F)

```

The reference data used to establish the peer building population in the United States is Fannie Mae’s Multifamily Energy and Water Market Research Survey.

```{r, warning=FALSE}
multifamily = read_csv("data/cbecs/FannieMae/mewmr-survey-database_data.csv")

## remove all special chars 
cols = names(multifamily)
cols <- gsub("[^0-9A-Za-z// ]","" , cols ,ignore.case = TRUE)
cols = gsub("  ", "", cols, fixed = TRUE)
names(multifamily) = make.names(cols, unique = T)

cols = c( "Total.gross.floor.area",
           "Total.number.of.units",
           "Unit.Density",
           "Bedrooms.Unit",
           "Number.of.BRs",
           "CDD", 
           "HDD",
           "Building.Type.Property.Level",
           "Total.SOURCE.kBtu",
           "Total.SITE.kBtu",
           "Source.EUI.using.Total.gross.floor.area",
           "Site.EUIusing.Total.gross.floor.area",
           "Survey.Weights.for.ENERGY.STAR.score.analysis")


```


## Apply filters

As per Energy Star's technical document [ENERGY STAR Score for Multifamily Housing in the United States](https://www.energystar.gov/buildings/tools-and-resources/energy_star_score_multifamily_housing_united_states), following filters are applied to define the peer group and to remove any outliers.

After applying each filter, the number of remaining buildings in the dataset (_Number Remaining: X_) and any difference (_Difference: X_) in count from the original Energy Star's technical documentation is also given. 


#. **Must have complete data for whole-property energy use and operating characteristics**
<br/>EPA Program Filter – Complete data is necessary for analysis.
<br/>Number Remaining: 357
<br/>Difference: +7.
    ```{r}
m0a = multifamily %>% 
  filter(Energy.Space.Served == "Whole property") %>%
  filter(X12.months.of.energy.data.provided == "Y") %>%
  #filter(Survey.Weights.for.ENERGY.STAR.score.analysis > 0) %>% 
  filter(Total.gross.floor.area > 0) %>% 
  filter(Total.number.of.units > 0) %>%
  filter(Unit.Density > 0) %>% 
  filter(Number.of.BRs > 0) %>%
  filter(Bedrooms.Unit > 0) %>%
  filter(CDD > 0) %>% 
  filter(HDD > 0) %>% 
  filter(Building.Type.Property.Level != "Not Provided")

m0b = m0a %>% 
  filter(Total.SOURCE.kBtu > 0) %>%
  filter(Total.SITE.kBtu > 0) %>%
  filter(Source.EUI.using.Total.gross.floor.area > 0)
  
m0c = m0b %>% filter( Total.number.of.units > 0 &
                        Unit.Density > 0 & 
                        Bedrooms.Unit > 0 & 
                        CDD > 0 & 
                        HDD > 0 )

    ```


#. **Must have at least 20 units**
<br/>Analytical filter – Analysis could not model behavior for buildings with fewer than 20 units, due to limited data.
<br/>Number Remaining: 351.
<br/>Difference: +9
    ```{r}
m1 = m0c %>% filter(Total.number.of.units >= 20)
    ```


#. **Source EUI must be less than 290 kBtu/ft2**
<br/>Analytical filter – Values determined to be data entry errors or statistical outliers.
<br/>Number Remaining: 347.
<br/>Difference: +14.
    ```{r}
m2 = m1 %>% filter(Source.EUI.using.Total.gross.floor.area > 0 & 
                     Source.EUI.using.Total.gross.floor.area < 290)
    ```


#. **Gross Floor area must be no more than 2,000,000 ft2**
<br/>Analytical filter – Values determined to be data entry errors or statistical outliers.
<br/>Number Remaining: 346
<br/>Difference: +14.
    ```{r}
m3 = m2 %>% filter(Total.gross.floor.area <= 2000000)
    ```


#. **Unit density must be less than 2.75 units per 1,000 square feet**
<br/>Analytical filter – Values determined to be data entry errors or statistical outliers.
<br/>Number Remaining: 338.
<br/>Difference: +11.
    ```{r}
m4 = m3 %>% filter(Unit.Density < 2.75)
    ```

#. **Bedroom Density must be more than 0.5 and less than 3.5 bedrooms per 1,000 square feet**
<br/>Analytical filter – Values determined to be data entry errors or statistical outliers.
<br/>Number Remaining: 336
<br/>Difference: +12.
    ```{r}
m5 = m4 %>% filter(Bedrooms.Unit > 0.5 & Bedrooms.Unit < 3.5)
    ```

#. **Other filters - Survey weights should be positive**
<br/>Number Remaining: 321
<br/>Difference: -1.
    ```{r}
m6 = m5 %>% filter(Unit.Density > 0 & 
                     Bedrooms.Unit > 0 & 
                     CDD > 0 & 
                     HDD > 0 & 
                     Survey.Weights.for.ENERGY.STAR.score.analysis > 0)
    ```

**Save the filtered dataset**
```{r}
m7 = m6[, cols]
write.csv(m7, paste0(filtered_dir, building_type, ".csv"), row.names = F)
```


## Prepare features

The final regression equation includes the following variables: 
 
 - Number of Units per 1,000 square feet
 - Number of Bedrooms per Unit
 - Total Heating Degree Days
 - Total Cooling Degree Days
 - Low-Rise building (yes/no)

```{r}
multifamily = read.csv(paste0(filtered_dir, building_type, ".csv"))

data = multifamily %>% 
  mutate(IsLowRise = 
           ifelse(Building.Type.Property.Level == "Low-rise", "Yes", "No")) 

ivars = c( "Total.gross.floor.area",
           "Unit.Density",
           "Bedrooms.Unit",
           "CDD", 
           "HDD", 
           "IsLowRise")

dvars = c("Total.SITE.kBtu",
          "Total.SOURCE.kBtu",
          "Site.EUIusing.Total.gross.floor.area",
          "Source.EUI.using.Total.gross.floor.area",
          "Survey.Weights.for.ENERGY.STAR.score.analysis")

features = data %>% 
  dplyr::select(c(ivars, dvars)) %>%
  dplyr::rename(SQFT = Total.gross.floor.area) %>%
  dplyr::rename(SITE_ENERGY = Total.SITE.kBtu) %>%
  dplyr::rename(SOURCE_ENERGY = Total.SOURCE.kBtu) %>%
  dplyr::rename(SITE_EUI = Site.EUIusing.Total.gross.floor.area) %>%
  dplyr::rename(SOURCE_EUI = Source.EUI.using.Total.gross.floor.area) %>%
  dplyr::rename(FINALWT = Survey.Weights.for.ENERGY.STAR.score.analysis) %>%
  dplyr::select(-c(SITE_EUI, SITE_ENERGY))

#summary(features)
features = features %>% na.omit()

write.csv(features, 
          paste0(features_dir, building_type, ".csv"), 
          row.names = F)

```

## Descriptive statistics 

```{r include=FALSE}
library(knitr)
opts_chunk$set(results = 'asis',      
              comment = NA, 
              prompt = FALSE, 
              cache = FALSE)

library(summarytools)
st_options(plain.ascii = FALSE,       
            style = "rmarkdown",      
            footnote = NA,            
            subtitle.emphasis = FALSE)                                    
st_css()                              
```


```{r}
features1 = features
features1 = features1 %>% dplyr::select(-one_of('SOURCE_ENERGY', 'FINALWT'))

summarytools::descr(features1, stats = "common", 
                    transpose = TRUE, 
                    headings = FALSE)
```


```{r}
dfSummary(features1, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE)
```


**Extract R code from Rmd document**
```{r}
#knitr::purl("multifamily.Rmd", output = "multifamily.R", documentation = 2)
```



## Build predictive models

```{r}
#source("models.R")
source("metrics.R")

data = read.csv(paste0(features_dir, building_type, ".csv"))

allMetrics = NULL

sourceEUI_attributes = setdiff(colnames(data),
                               c("SQFT", "FINALWT", "SOURCE_EUI", "SOURCE_ENERGY"))

sourceEnergy_attributes = setdiff(colnames(data), 
                               c("FINALWT", "SOURCE_EUI", "SOURCE_ENERGY"))
#cat(colnames(data))
knitr::kable(colnames(data), col.names = NULL)

```


### Multiple Linear Regression (MLR)

```{r}
MLR.fit <- function(data, 
                    x, 
                    y, 
                    w, 
                    interaction,
                    centering = TRUE 
                    ) {
  
  if(centering == TRUE){
    data = mean_center_data(data, x)  
  }
  
  if(interaction == 1) {  ### ordinary model
    model = paste(y, "~", paste(x, collapse = " + "))  
  } else {  ### interaction model
    allvars = paste(x, collapse = " + ")
    model = paste(y, "~ (", allvars, ") ^", interaction )
  }
  
  fit = lm(model, data = data, weights = data[, w])
  return (fit)
}

MLR.predict <- function(data, x, y, w, i) {
  
  mlrFit = MLR.fit(data, x, y, w, i)
  
  wt   = data[, w]
  obs  = data[, y]
  pred = as.numeric(predict(mlrFit))
  
  mlrMetrics = getMLRmetrics(mlrFit, obs, pred, wt)
  mlrMetrics = data.frame(
    "model" = "MLR",
    "dependent" = y,
    "interaction" = i,
    "transform" = "meanCent",
    mlrMetrics)
  
  return(mlrMetrics)
}

```


#### Using SOURCE_EUI as dependent variable
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"
interaction = 1

mlrMetrics = MLR.predict(data, x, y, w, interaction)

allMetrics = rbind(allMetrics, mlrMetrics)

knitr::kable(allMetrics, row.names = F)

```


#### Using SOURCE_ENERGY as dependent variable
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"
interaction = 1

mlrMetrics = MLR.predict(data, x, y, w, interaction)

allMetrics = rbind(allMetrics, mlrMetrics)

knitr::kable(allMetrics, row.names = F)

```


### Multiple Linear Regression (MLR) with Interaction terms

#### Using SOURCE_EUI as dependent variable
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"

intr_depth = length(x)

for (interaction in 2:intr_depth) {
  mlrMetrics = MLR.predict(data, x, y, w, interaction)
  allMetrics = rbind(allMetrics, mlrMetrics)
}

write.csv(allMetrics, 
          paste0(results_dir, building_type, ".csv"), 
          row.names = F)

allMetrics0 = allMetrics %>% filter(dependent == y)
knitr::kable(allMetrics0, row.names = F)

```

#### Using SOURCE_ENERGY as dependent variable**
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"

intr_depth = length(x)

for (interaction in 2:intr_depth) {
  mlrMetrics = MLR.predict(data, x, y, w, interaction)
  allMetrics = rbind(allMetrics, mlrMetrics)
}

write.csv(allMetrics, 
          paste0(results_dir, building_type, ".csv"), 
          row.names = F)

allMetrics0 = allMetrics %>% filter(dependent == y)
knitr::kable(allMetrics0, row.names = F)

```


### Comparision of MLR models

#### MLR plots using Source EUI
```{r, warning=FALSE}
mytheme = theme(legend.title = element_blank(),
           legend.text=element_text(size=12),
           axis.text=element_text(size=12),
           text=element_text(size=12))

plotR2 <- function(df, titl) {
  
  df1 = melt(df, measure.vars = c("R.2", "Adj.R.2"))
  
  plot <- ggplot(df1, aes(x = interaction, y=value, 
                          group=variable, col=variable)) + 
  geom_point(size=2) + geom_line(size=1) +
    ggtitle(titl) + 
    theme_pubr(base_size=12) +
    theme(legend.position="top", legend.title = element_blank())
  
  return(plot)
}

plotNRMSE <- function(df, titl) {
  
  df1 = melt(df, measure.vars = c("nrmse_iqr", "nrmse_mean", 
                                        "nrmse_sd"))
  df1$variable = toupper(df1$variable)
  
  plot <- ggplot(df1, aes(x = interaction, y=value, 
                          group=variable, col=variable)) + 
  geom_point(size=2) + geom_line(size=1) +
    ggtitle(titl) + 
    theme_pubr(base_size=12) +
    theme(legend.position="top", legend.title = element_blank())
    
  
  return(plot)
}  

```

```{r}

allMetrics0 = allMetrics %>%
  filter(stringr::str_detect(model, "MLR")) %>%
  filter(dependent == "SOURCE_EUI")

plot1 = plotR2(allMetrics0, "MLR models using source EUI")
plot2 = plotNRMSE(allMetrics0, "MLR models using source EUI")

print(plot1)
print(plot2)

```


#### MLR plots using Source Energy
```{r}

allMetrics0 = allMetrics %>%
  filter(stringr::str_detect(model, "MLR")) %>%
  filter(dependent == "SOURCE_ENERGY")

plot1 = plotR2(allMetrics0, "MLR models using source energy")
plot2 = plotNRMSE(allMetrics0, "MLR models using source energy")

print(plot1)
print(plot2)

```



### Gradient Boosted Trees (XGBoost)

```{r}

tuneXGBoost <- function(x,
                        y,
                        sample_weights,
                        search = "default",
                        tree_height = 2
                        ) {
  
  N = 10  # N-fold CV
  R = 2   # and R repeats
  
  tcDefault  <- trainControl(method = "repeatedcv", 
                            number = N, 
                            repeats = R)
  
  tcRandom   <- trainControl(method = "repeatedcv", 
                            search = "random",
                            number = N, 
                            repeats = R)
  
  tcAdaptive <- trainControl(method = "adaptive_cv", 
                            search = "random",
                            number = N, 
                            repeats = R,
                            adaptive = list(min = 5, 
                                            alpha = 0.05, 
                                            method = "gls",
                                            complete = TRUE))
  
  default_param = expand.grid(
    nrounds = 100,
    max_depth = tree_height,
    eta = 0.3,
    gamma = 0,
    colsample_bytree = 1,
    min_child_weight = 1,
    subsample = 1)
  
  # from https://github.com/topepo/caret/blob/master/models/files/xgbTree.R
  len = 10
  grid_param <- expand.grid(
    nrounds = floor((1:len) * 10),
    max_depth = tree_height,
    eta = c(.3, .4),
    gamma = 0,
    colsample_bytree = c(.6, .8),
    min_child_weight = c(1),
    subsample = seq(.25, 1, length = len))
  
  tuned = switch(search,
                 "default" = train(x, y,
                                   weights = sample_weights,
                                   method = "xgbTree", 
                                   tuneGrid = default_param,
                                   trControl = tcDefault,
                                   verbose = TRUE),
                 
                 "grid"     = train(x, y, 
                                   weights = sample_weights,
                                   method = "xgbTree", 
                                   tuneGrid = grid_param,
                                   trControl = tcDefault,
                                   verbose = TRUE),

                 "random"  = train(x, y, 
                                   weights = sample_weights,
                                   method = "xgbTree", 
                                   trControl = tcRandom,
                                   verbose = TRUE),
                 
                 "adaptive" = train(x, y, 
                                   weights = sample_weights,
                                   method = "xgbTree", 
                                   trControl = tcAdaptive,
                                   verbose = TRUE)
                 )
  
  return(tuned$finalModel)
}

XGBoost <- function( xdata, 
                     ydata,
                     sample_weights,
                     search = "default",
                     interaction = 2
                     ) {
  
  model = paste(y, "~", paste(x, collapse = " + "))
  dummy = dummyVars(model, data = data, fullRank = T)
  
  xdata = as.data.frame(predict(dummy, data))
  ydata = data[, y]
  
  xgfit = tuneXGBoost(xdata, ydata, 
                      sample_weights,
                      search, 
                      tree_height = interaction)
  return(xgfit)
} 


XGBoost.predict <- function(data, x, y, w, search) {

  model = paste(y, "~", paste(x, collapse = " + "))
  dummy = dummyVars(model, data = data, fullRank = T)
  xdata = as.data.frame(predict(dummy, data))
  ydata = data[, y]
  wt = data[, w]
  
  intr_depth = 3
  
  xgbMetricsAll = NULL
  
  for (intr in 1:intr_depth) {
    
    cat(paste(Sys.time(), "xgboost", search, y, intr, "\n"))
    
    xgfit = XGBoost(xdata, ydata, wt, 
                    search = search, 
                    interaction = intr)
    
    pred = as.numeric(predict(xgfit, as.matrix(xdata)))
    
    xgbMetrics = getXgboostmetrics(xgfit, xdata, ydata, pred, wt)
    
    xgbMetrics = data.frame(
      "model" = paste0("XGB", substr(search, 1,1), intr),
      "dependent" = y, 
      "interaction" = intr, 
      "transform" = "None",
      xgbMetrics)
    
    xgbMetricsAll = rbind(xgbMetricsAll, xgbMetrics)
  }
  
  return(xgbMetricsAll)
}

```

```{r}
# y = "SOURCE_EUI"
# w = "FINALWT"
# o = c("SOURCE_ENERGY", "SQFT")
# x = setdiff(colnames(data), c(y, w, o))
# wt = data[, w]
# 
# model = paste(y, "~", paste(x, collapse = " + "))
# dummy = dummyVars(model, data = data, fullRank = T)
# xdata = as.data.frame(predict(dummy, data))
# ydata = data[, y]
# intr_depth = 3
# 
# for (intr in 1:intr_depth) {
#   
#   print(paste(Sys.time(), "xgboost default search", y, intr, "\n"))
#   
#   xgfit = XGBoost(xdata, ydata, wt, 
#                   search = "default", 
#                   interaction = intr)
#   
#   pred = as.numeric(predict(xgfit, as.matrix(xdata)))
#   
#   xgbMetrics = getXgboostmetrics(xgfit, xdata, ydata, pred, wt)
#   
#   xgbMetrics = data.frame(
#     "model" = paste0("XGBd", intr),
#     "dependent" = y, 
#     "interaction" = intr, 
#     "transform" = "None",
#     xgbMetrics)
#   
#   allMetrics = rbind(allMetrics, xgbMetrics)
# }
# knitr::kable(allMetrics, row.names = F)

```

#### Using SOURCE_EUI as dependent variable

```{r, warning=FALSE}
library(doParallel)
ncore = 4
registerDoParallel(cores = ncore)
```

##### Using default search
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"
search = "default"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```

##### Using grid search
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"
search = "grid"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```


##### Using adaptive search
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"
search = "adaptive"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```


##### Using random search
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"
search = "random"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

write.csv(allMetrics, 
          paste0(results_dir, building_type, ".csv"), 
          row.names = F)

allMetrics0 = allMetrics %>% filter(dependent == y)
knitr::kable(allMetrics0, row.names = F)

```


#### Using SOURCE_ENERGY as dependent variable


##### Using default search
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"
search = "default"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```


##### Using grid search
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"
search = "grid"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```


##### Using adaptive search
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"
search = "adaptive"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```


##### Using random search
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"
search = "random"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

write.csv(allMetrics, 
          paste0(results_dir, building_type, ".csv"), 
          row.names = F)

allMetrics0 = allMetrics %>% filter(dependent == y)
knitr::kable(allMetrics0, row.names = F)

```




### Comparision of XGB models

```{r, warning=FALSE}
plotXgbR2 <- function(df, titl) {
  
  plot <- ggplot(df, aes(x = interaction, y=Adj.R.2, 
                          group=model, col=model)) + 
    geom_point(size=2) + geom_line(size=1) +  
    ggtitle(titl) + 
    theme_pubr(base_size=12) +
    theme(legend.position="top", legend.title = element_blank()) 

  return(plot)
}

plotXgbNRMSE <- function(df, titl) {
  
  df1 = melt(df, measure.vars = c("nrmse_iqr", "nrmse_mean", 
                                        "nrmse_sd"))
  df1$variable = toupper(df1$variable)
  plot <- ggplot(df1, aes(x = interaction, y=value, 
                          group=variable, col=variable)) + 
  geom_point(size=2) + geom_line(size=1) +
    facet_wrap(. ~ model, scales = "fixed", nrow=2) + 
    ggtitle(titl) + 
    theme_pubr(base_size=12) +
    theme(legend.position="top", legend.title = element_blank()) + 
    theme(strip.placement = "outside", strip.background = element_blank())
  
  return(plot)
}
```

#### XGB plots using Source EUI
```{r}
allMetrics0 = allMetrics %>%
  mutate(model = substr(model, 1, 4)) %>%
  filter(stringr::str_detect(model, "XGB")) %>%
  filter(dependent == "SOURCE_EUI")

plot1 = plotXgbR2(allMetrics0, "XGB models using source EUI")
plot2 = plotXgbNRMSE(allMetrics0, "XGB models using source EUI")

print(plot1)
print(plot2)

```

#### XGB plots using Source Energy
```{r}
allMetrics0 = allMetrics %>%
  mutate(model = substr(model, 1, 4)) %>%
  filter(stringr::str_detect(model, "XGB")) %>%
  filter(dependent == "SOURCE_ENERGY")

plot1 = plotXgbR2(allMetrics0, "XGB models using source energy")
plot2 = plotXgbNRMSE(allMetrics0, "XGB models using source energy")

print(plot1)
print(plot2)

```


### Comparision between MLR and XGB models

#### MLR and XGB plots using Source EUI
```{r}
allMetrics0 = allMetrics %>%
  mutate(model = substr(model, 1, 4)) %>%
  #filter(stringr::str_detect(model, "XGB")) %>%
  filter(dependent == "SOURCE_EUI")

plot1 = plotXgbR2(allMetrics0, "Comparison MLR and XGB models using source EUI")
plot2 = plotXgbNRMSE(allMetrics0, "Comparison MLR and XGB models using source EUI")

print(plot1)
print(plot2)

```

#### MLR and XGB plots using Source Energy
```{r}
allMetrics0 = allMetrics %>%
  mutate(model = substr(model, 1, 4)) %>%
  #filter(stringr::str_detect(model, "XGB")) %>%
  filter(dependent == "SOURCE_ENERGY")

plot1 = plotXgbR2(allMetrics0, "Comparison MLR and XGB models using source energy")
plot2 = plotXgbNRMSE(allMetrics0, "Comparison MLR and XGB models using source energy")

print(plot1)
print(plot2)

```
