---
title: "Benchmarking Retail stores and Supermarkets"
author: "Pandarasamy Arjunan"
date: "3 June 2019"
output: 
  github_document:
    toc: true
#  html_document:
#    code_folding: "hide"
#    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(Metrics)
library(caret)
library(xgboost)
library(ggplot2)
library(reshape2)
library(ggpubr)
```



## Load dataset

```{r message=FALSE, warning=FALSE}
building_type = "retail"

filtered_dir = './data/cbecs/filtered/'
dir.create(filtered_dir, recursive = T, showWarnings = F)

features_dir = './data/cbecs/features/'
dir.create(features_dir, recursive = T, showWarnings = F)

results_dir = './results/cbecs/'
dir.create(results_dir, recursive = T, showWarnings = F)
```

```{r}
cbecs = read.csv("data/cbecs/2012_public_use_data_aug2016.csv")

## list of building attributes relevant to office buildings 
var1 = c( 'SQFT', 'NFLOOR', 'NELVTR', 'NESLTR', 'COURT',
          'MONUSE', 'WKHRS', 'NWKER', 'COOK', 'HEATP',
          'COOLP', 'SNACK', 'FASTFD', 'CAF', 'FDPREP',
          'KITCHN', 'BREAKRM', 'OTFDRM', 'RFGSTO', 'RFGWIN',
          'RFGOPN', 'RFGCLN', 'RFGVNN', 'RFGICN', 'RFGSTP',
          'PCTERMN', 'LAPTPN', 'PRNTRN',  'SERVERN',
          'TVVIDEON', 'RGSTRN', 'COPIERN',  'HDD65', 'CDD65',
          'RFGRES')

var2 = c( "PBAPLUS", "PBA", "FINALWT",
          "MFBTU", 
          "ELBTU", "NGBTU", "FKBTU", "DHBTU",
          "ONEACT", "ACT1", "ACT2", "ACT3", "ACT1PCT", "ACT2PCT", "ACT3PCT",
          "PRAMTC", "PRUNIT",
          "CWUSED", "WOUSED", "COUSED", "SOUSED", "PRUSED")

var3 = c( "RFGRSN", "RFGCOMPN", "RFGWIN", "RFGOPN", "RFGCLN", "RFGVNN")

# imputed data details
var4 = c("ZWKHRS", "ZNWKER", "ZRFGWIN", "ZCOOLP", "ZHEATP")

# heat details
var5 = c("HEATP", "FURNP", "PKGHP", "BOILP", "STHWP", "HTPHP", "SLFCNP", "OTHTP")

retail = cbecs[, c(var1, var2, var3, var4, var5)]
```


## Apply filters

As per Energy Star's technical document [ENERGY STAR Score for Retail Stores and Supermarkets](https://www.energystar.gov/buildings/tools-and-resources/energy-star-score-retail-stores), following filters are applied to define the peer group and to remove any outliers.

After applying each filter, the number of remaining buildings in the dataset (_Number Remaining: X_) and any difference (_Difference: X_) in count from the original Energy Star's technical documentation is also given. 


#. **Calculate source energy and source EUI**
    ```{r}
## convert electricity, natural gas, fuel oil, and district heat to source energy
r0 = retail %>% 
  mutate(ELBTU0 = ELBTU*2.80) %>%
  mutate(NGBTU0 = NGBTU*1.05) %>%
  mutate(FKBTU0 = FKBTU*1.01) %>%
  mutate(DHBTU0 = DHBTU*1.20) %>%
  mutate(SOURCE_ENERGY = rowSums(dplyr::select(., c(ELBTU0,NGBTU0,FKBTU0,DHBTU0)), na.rm = T)) %>% 
  mutate(SOURCE_EUI = round(SOURCE_ENERGY/SQFT, 2)) %>%
  mutate(SITE_EUI = round(MFBTU/SQFT, 2)) %>%
  mutate(NGBTU_PERCENT = round(NGBTU / SOURCE_ENERGY * 100, 2)) %>% 
  mutate(SUMBTU = rowSums(dplyr::select(., c(ELBTU,NGBTU,FKBTU,DHBTU)), na.rm = T))

#Is MFBTU the sum of ELBTU,NGBTU,FKBTU,DHBTU? YES.
#summary(o14$MFBTU - o14$SUMBTU)

    ```


#. **PBAPLUS= 14 or 42**
<br/>Building Filter – CBECS defines building types according to the variable “PBAPLUS.” Retail Stores are coded as PBAPLUS = 42 and Supermarkets are coded as PBAPLUS = 14.
<br/>Number Remaining: 342.
<br/>Difference: 0.
    ```{r}
    r1 = r0 %>% filter(PBAPLUS %in% c(14, 42))
    ```

#. **Must operate for at least 30 hours per week**
<br/>EPA Program Filter – Baseline condition for being a full time retail store or supermarket.
<br/>Number Remaining: 335.
<br/>Difference: 0.
    ```{r}
    r2 = r1 %>% filter(WKHRS >= 30)
    ```

#. **Must have at least 1 worker**
<br/>EPA Program Filter – Baseline condition for being a full time retail store or supermarket.
<br/>Number Remaining: 335.
<br/>Difference: 0.
    ```{r}
    r3 = r2 %>% filter(NWKER >= 1)
    ```    

#. **Must have at least 1 computer or cash register**
<br/>EPA Program Filter – Baseline condition for being a full time retail store or supermarket.
<br/>Number Remaining: 323.
<br/>Difference: 0.
    ```{r}
    r4 = r3 %>% filter(PCTERMN >= 1 | RGSTRN >=1)
    ```

#. **If building is a supermarket, must have refrigeration equipment**
<br/>EPA Program Filter – Baseline condition for being a full time supermarket.
<br/>Number Remaining: 323.
<br/>Difference: 0.
    ```{r}
    r5 = r4 %>% 
      filter( PBAPLUS != "03" | RFGRES == 1)
    ```    

#. **Must operate for at least 10 months per year**
<br/>EPA Program Filter – Baseline condition for being a full time retail store.
<br/>Number Remaining: 311.
<br/>Difference: 0.
    ```{r}
    r6 = r5 %>% filter(MONUSE >= 10)
    ```

#. **A single activity must characterize more than 50% of the floor space**
<br/>EPA Program Filter – In order to be considered part of the retail store and supermarket peer group, more than 50% of the building must be defined as a retail store or supermarket.
<br/>If the variable ONEACT=1, this indicates that one activity occupies 75% or more of the building. If the variable ONEACT=2, then the building can specify up to 3 activities (ACT1, ACT2, ACT3). One of these activities must be Food Sales or Service (PBAX=14) or Retail (Other Than Mall) (PBAX=16), with a corresponding percent (ACT1PCT, ACT2PCT, ACT3PCT) that is greater than 50.
<br/>Number Remaining: 306.
<br/>Difference: +5.
    ```{r}
r7 = r6 %>% 
  filter( (ONEACT == 1) |
            (ONEACT == 2 & 
               ((ACT1 %in% c(14,16) & ACT1PCT > 50) | 
                  (ACT2 %in% c(14,16) & ACT2PCT > 50) | 
                  (ACT3 %in% c(14,16) & ACT3PCT > 50) )))
    ```    

#. **Must be less than or equal to 1,000,000 square feet**
<br/>Data Limitation Filter – CBECS masks surveyed properties above 1,000,000 square feet by applying regional averages.
<br/>Number Remaining: 306.
<br/>Difference: +5.
    ```{r}
    r8 = r7 %>% filter(SQFT <= 1000000)
    ```    

#. **If propane is used, the amount category (PRAMTC) must equal 1, 2, or 3**
<br/>Data Limitation Filter – Cannot estimate propane use if the quantity is “greater than 1000” or unknown.
<br/>Number Remaining: 294.
<br/>Difference: +5.
    ```{r}
    r9 = r8 %>% filter(is.na(PRAMTC) | PRAMTC %in% c(1,2,3))
    ```        

#. **If propane is used, the unit (PRUNIT) must be known**
<br/>Data Limitation Filter – Cannot estimate propane use if the unit is unknown.
<br/>Number Remaining: 292.
<br/>Difference: +5.
    ```{r}
    r10 = r9 %>% filter(is.na(PRUNIT) | PRUNIT %in% c(1,2))
    ```    

#. **If propane is used, the maximum estimated propane amount must be 10% or less of the total source energy**
<br/>Data Limitation Filter – Because propane values are estimated from a range, propane is restricted to 10% of the total source energy.
<br/>Number Remaining: 289.
<br/>Difference: +7.
    ```{r}
    r11 = r10 %>% 
      filter( PRUSED == 2 | is.na(NGBTU_PERCENT) == T | 
                (PRUSED == 1 & NGBTU_PERCENT <= 10))

    ```    

#. **must not use chilled water, wood, coal, or solar**
<br/>Data Limitation Filter – CBECS does not collect quantities of chilled water, wood, coal, or solar.
<br/>Number Remaining: 282.
<br/>Difference: +8.
    ```{r}
    r12 = r11 %>% 
      filter(CWUSED == 2) %>%
      filter(WOUSED == 2) %>% 
      filter(COUSED == 2) %>% 
      filter(SOUSED == 2)
    ```    


#. **Must be at least 5,000 square feet**
<br/>Analytical Limitation – Analysis could not model behavior for buildings smaller than 5,000 ft2.
<br/>Number Remaining: 201.
<br/>Difference: +5.
    ```{r}
    r13 = r12 %>% filter(SQFT >= 5000)
    ```
    

#. **Must have fewer than 3 open or closed refrigeration/freezer cases per 1,000 square feet**
<br/>Analytical Filter – Values determined to be statistical outliers.
<br/>Number Remaining: 201.
<br/>Difference: +6.
    ```{r}
    r14 = r13 %>% filter( (is.na(RFGOPN) | (RFGOPN/SQFT * 1000 < 3)) | 
                          (is.na(RFGCLN) | (RFGCLN/SQFT * 1000 < 3)))
    ```


#. **Must have fewer than 0.7 walk-in refrigeration/freezer cases per 1,000 square feet**
<br/>Analytical Filter – Values determined to be statistical outliers.
<br/>Number Remaining: 201.
<br/>Difference: +6.
    ```{r}
    r15 = r14 %>% filter(is.na(RFGWIN) | (RFGWIN / SQFT * 1000 <= 0.7)) 
    ```    
    
#. **Must have Source EUI greater than or equal to 20 kBtu/ft2**
<br/>Analytical Filter – Values determined to be statistical outliers.
<br/>Number Remaining: 196.
<br/>Difference: +4.
    ```{r}
    r16 = r15 %>% filter( SOURCE_EUI >= 20)
    ```    

#. **If CDD is greater than 3,000, must be at least 60% cooled**
<br/>Analytical Filter – Values determined to be statistical outliers.
<br/>Number Remaining: 193.
<br/>Difference: +4.
    ```{r}
    r17 = r16 %>% filter( CDD65 <= 3000 | COOLP >= 60) 
    ```

**Save the filtered dataset**
```{r}
write.csv(r17, paste0(filtered_dir, building_type, ".csv"), row.names = F)
```    


## Prepare features

The final regression equation includes the following variables: 

 - Weekly Operating Hours
 - Number of Workers per 1,000 Square Feet
 - Number of Commercial Refrigeration/Freezer Units per 1,000 Square Feet
 - Natural log of Heating Degree Days times Percent of the Building that is Heated
 - Natural log of Cooling Degree Days times Percent of the Building that is Cooled
 - Yes/No variable indicating whether the Building is a Supermarket (1 = yes, 0 = no)
- Adjustment for the Number of Workers per 1,000 Square Feet for a Supermarket

```{r}
retail = read.csv(paste0(filtered_dir, building_type, ".csv"))

data = retail %>%
  dplyr::mutate(NWKER_SQFT = NWKER/SQFT * 1000) %>%
  dplyr::mutate(RFG_TOT = rowSums(dplyr::select(., c(RFGRSN,RFGCOMPN,RFGWIN,RFGOPN,RFGCLN,RFGVNN)), na.rm = T)) %>% 
  dplyr::mutate(RFG_SQFT = RFG_TOT/SQFT * 1000) %>%
  dplyr::mutate(CDD65_COOLP = log(CDD65) * COOLP / 100) %>%
  dplyr::mutate(HDD65_HEATP = log(HDD65) * HEATP / 100) %>%
  dplyr::mutate(IsSuperMarket = ifelse(PBAPLUS == 14, "Yes", "No")) %>%
  dplyr::mutate(AdjNWKER_SQFTsuperMarket = ifelse(PBAPLUS == 14, 1, 0)) %>%
  dplyr::mutate(AdjNWKER_SQFTsuperMarket = AdjNWKER_SQFTsuperMarket * NWKER_SQFT) %>%
  dplyr::mutate_if(is.numeric, round, 3)

#TODO: Adjustment for the Number of Workers per 1,000 Square Feet for a Supermarket

ivars = c(
  "SQFT",
  "WKHRS", "NWKER_SQFT", "RFG_SQFT", 
          "HDD65_HEATP", "CDD65_COOLP", 
          "IsSuperMarket", "AdjNWKER_SQFTsuperMarket")

dvars  = c("SOURCE_EUI", "SOURCE_ENERGY", "FINALWT")

features = data[, c(ivars, dvars)]
features = features %>% na.omit()

write.csv(features, 
          paste0(features_dir, building_type, ".csv"), 
          row.names = F)

```


## Descriptive statistics 
```{r include=FALSE}
library(knitr)
opts_chunk$set(results = 'asis',      
              comment = NA, 
              prompt = FALSE, 
              cache = FALSE)

library(summarytools)
st_options(plain.ascii = FALSE,       
            style = "rmarkdown",      
            footnote = NA,            
            subtitle.emphasis = FALSE)                                    
st_css()                              
```

```{r}
features1 = features
features1 = features1 %>% dplyr::select(-one_of('SOURCE_ENERGY', 'FINALWT'))

summarytools::descr(features1, stats = "common", 
                    transpose = TRUE, 
                    headings = FALSE)
```


```{r}
dfSummary(features1, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE)
```


**Extract R code from Rmd document**
```{r}
#knitr::purl("retail.Rmd", output = "retail.R", documentation = 2)
```



## Build predictive models

```{r}
#source("models.R")
source("metrics.R")

data = read.csv(paste0(features_dir, building_type, ".csv"))

allMetrics = NULL

sourceEUI_attributes = setdiff(colnames(data),
                               c("SQFT", "FINALWT", "SOURCE_EUI", "SOURCE_ENERGY"))

sourceEnergy_attributes = setdiff(colnames(data), 
                               c("FINALWT", "SOURCE_EUI", "SOURCE_ENERGY"))
#cat(colnames(data))
knitr::kable(colnames(data), col.names = NULL)

```


### Multiple Linear Regression (MLR)

```{r}
MLR.fit <- function(data, 
                    x, 
                    y, 
                    w, 
                    interaction,
                    centering = TRUE 
                    ) {
  
  if(centering == TRUE){
    data = mean_center_data(data, x)  
  }
  
  if(interaction == 1) {  ### ordinary model
    model = paste(y, "~", paste(x, collapse = " + "))  
  } else {  ### interaction model
    allvars = paste(x, collapse = " + ")
    model = paste(y, "~ (", allvars, ") ^", interaction )
  }
  
  fit = lm(model, data = data, weights = data[, w])
  return (fit)
}

MLR.predict <- function(data, x, y, w, i) {
  
  mlrFit = MLR.fit(data, x, y, w, i)
  
  wt   = data[, w]
  obs  = data[, y]
  pred = as.numeric(predict(mlrFit))
  
  mlrMetrics = getMLRmetrics(mlrFit, obs, pred, wt)
  mlrMetrics = data.frame(
    "model" = "MLR",
    "dependent" = y,
    "interaction" = i,
    "transform" = "meanCent",
    mlrMetrics)
  
  return(mlrMetrics)
}

```


#### Using SOURCE_EUI as dependent variable
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"
interaction = 1

mlrMetrics = MLR.predict(data, x, y, w, interaction)

allMetrics = rbind(allMetrics, mlrMetrics)

knitr::kable(allMetrics, row.names = F)

```


#### Using SOURCE_ENERGY as dependent variable
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"
interaction = 1

mlrMetrics = MLR.predict(data, x, y, w, interaction)

allMetrics = rbind(allMetrics, mlrMetrics)

knitr::kable(allMetrics, row.names = F)

```


### Multiple Linear Regression (MLR) with Interaction terms

#### Using SOURCE_EUI as dependent variable
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"

intr_depth = length(x)

for (interaction in 2:intr_depth) {
  mlrMetrics = MLR.predict(data, x, y, w, interaction)
  allMetrics = rbind(allMetrics, mlrMetrics)
}

write.csv(allMetrics, 
          paste0(results_dir, building_type, ".csv"), 
          row.names = F)

allMetrics0 = allMetrics %>% filter(dependent == y)
knitr::kable(allMetrics0, row.names = F)

```

#### Using SOURCE_ENERGY as dependent variable**
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"

intr_depth = length(x)

for (interaction in 2:intr_depth) {
  mlrMetrics = MLR.predict(data, x, y, w, interaction)
  allMetrics = rbind(allMetrics, mlrMetrics)
}

write.csv(allMetrics, 
          paste0(results_dir, building_type, ".csv"), 
          row.names = F)

allMetrics0 = allMetrics %>% filter(dependent == y)
knitr::kable(allMetrics0, row.names = F)

```


### Comparision of MLR models

#### MLR plots using Source EUI
```{r, warning=FALSE}
mytheme = theme(legend.title = element_blank(),
           legend.text=element_text(size=12),
           axis.text=element_text(size=12),
           text=element_text(size=12))

plotR2 <- function(df, titl) {
  
  df1 = melt(df, measure.vars = c("R.2", "Adj.R.2"))
  
  plot <- ggplot(df1, aes(x = interaction, y=value, 
                          group=variable, col=variable)) + 
  geom_point(size=2) + geom_line(size=1) +
    ggtitle(titl) + 
    theme_pubr(base_size=12) +
    theme(legend.position="top", legend.title = element_blank())
  
  return(plot)
}

plotNRMSE <- function(df, titl) {
  
  df1 = melt(df, measure.vars = c("nrmse_iqr", "nrmse_mean", 
                                        "nrmse_sd"))
  df1$variable = toupper(df1$variable)
  
  plot <- ggplot(df1, aes(x = interaction, y=value, 
                          group=variable, col=variable)) + 
  geom_point(size=2) + geom_line(size=1) +
    ggtitle(titl) + 
    theme_pubr(base_size=12) +
    theme(legend.position="top", legend.title = element_blank())
    
  
  return(plot)
}  

```

```{r}

allMetrics0 = allMetrics %>%
  filter(stringr::str_detect(model, "MLR")) %>%
  filter(dependent == "SOURCE_EUI")

plot1 = plotR2(allMetrics0, "MLR models using source EUI")
plot2 = plotNRMSE(allMetrics0, "MLR models using source EUI")

print(plot1)
print(plot2)

```


#### MLR plots using Source Energy
```{r}

allMetrics0 = allMetrics %>%
  filter(stringr::str_detect(model, "MLR")) %>%
  filter(dependent == "SOURCE_ENERGY")

plot1 = plotR2(allMetrics0, "MLR models using source energy")
plot2 = plotNRMSE(allMetrics0, "MLR models using source energy")

print(plot1)
print(plot2)

```



### Gradient Boosted Trees (XGBoost)

```{r}

tuneXGBoost <- function(x,
                        y,
                        sample_weights,
                        search = "default",
                        tree_height = 2
                        ) {
  
  N = 10  # N-fold CV
  R = 2   # and R repeats
  
  tcDefault  <- trainControl(method = "repeatedcv", 
                            number = N, 
                            repeats = R)
  
  tcRandom   <- trainControl(method = "repeatedcv", 
                            search = "random",
                            number = N, 
                            repeats = R)
  
  tcAdaptive <- trainControl(method = "adaptive_cv", 
                            search = "random",
                            number = N, 
                            repeats = R,
                            adaptive = list(min = 5, 
                                            alpha = 0.05, 
                                            method = "gls",
                                            complete = TRUE))
  
  default_param = expand.grid(
    nrounds = 100,
    max_depth = tree_height,
    eta = 0.3,
    gamma = 0,
    colsample_bytree = 1,
    min_child_weight = 1,
    subsample = 1)
  
  # from https://github.com/topepo/caret/blob/master/models/files/xgbTree.R
  len = 10
  grid_param <- expand.grid(
    nrounds = floor((1:len) * 10),
    max_depth = tree_height,
    eta = c(.3, .4),
    gamma = 0,
    colsample_bytree = c(.6, .8),
    min_child_weight = c(1),
    subsample = seq(.25, 1, length = len))
  
  tuned = switch(search,
                 "default" = train(x, y,
                                   weights = sample_weights,
                                   method = "xgbTree", 
                                   tuneGrid = default_param,
                                   trControl = tcDefault,
                                   verbose = TRUE),
                 
                 "grid"     = train(x, y, 
                                   weights = sample_weights,
                                   method = "xgbTree", 
                                   tuneGrid = grid_param,
                                   trControl = tcDefault,
                                   verbose = TRUE),

                 "random"  = train(x, y, 
                                   weights = sample_weights,
                                   method = "xgbTree", 
                                   trControl = tcRandom,
                                   verbose = TRUE),
                 
                 "adaptive" = train(x, y, 
                                   weights = sample_weights,
                                   method = "xgbTree", 
                                   trControl = tcAdaptive,
                                   verbose = TRUE)
                 )
  
  return(tuned$finalModel)
}

XGBoost <- function( xdata, 
                     ydata,
                     sample_weights,
                     search = "default",
                     interaction = 2
                     ) {
  
  model = paste(y, "~", paste(x, collapse = " + "))
  dummy = dummyVars(model, data = data, fullRank = T)
  
  xdata = as.data.frame(predict(dummy, data))
  ydata = data[, y]
  
  xgfit = tuneXGBoost(xdata, ydata, 
                      sample_weights,
                      search, 
                      tree_height = interaction)
  return(xgfit)
} 


XGBoost.predict <- function(data, x, y, w, search) {

  model = paste(y, "~", paste(x, collapse = " + "))
  dummy = dummyVars(model, data = data, fullRank = T)
  xdata = as.data.frame(predict(dummy, data))
  ydata = data[, y]
  wt = data[, w]
  
  intr_depth = 3
  
  xgbMetricsAll = NULL
  
  for (intr in 1:intr_depth) {
    
    cat(paste(Sys.time(), "xgboost", search, y, intr, "\n"))
    
    xgfit = XGBoost(xdata, ydata, wt, 
                    search = search, 
                    interaction = intr)
    
    pred = as.numeric(predict(xgfit, as.matrix(xdata)))
    
    xgbMetrics = getXgboostmetrics(xgfit, xdata, ydata, pred, wt)
    
    xgbMetrics = data.frame(
      "model" = paste0("XGB", substr(search, 1,1), intr),
      "dependent" = y, 
      "interaction" = intr, 
      "transform" = "None",
      xgbMetrics)
    
    xgbMetricsAll = rbind(xgbMetricsAll, xgbMetrics)
  }
  
  return(xgbMetricsAll)
}

```

```{r}
# y = "SOURCE_EUI"
# w = "FINALWT"
# o = c("SOURCE_ENERGY", "SQFT")
# x = setdiff(colnames(data), c(y, w, o))
# wt = data[, w]
# 
# model = paste(y, "~", paste(x, collapse = " + "))
# dummy = dummyVars(model, data = data, fullRank = T)
# xdata = as.data.frame(predict(dummy, data))
# ydata = data[, y]
# intr_depth = 3
# 
# for (intr in 1:intr_depth) {
#   
#   print(paste(Sys.time(), "xgboost default search", y, intr, "\n"))
#   
#   xgfit = XGBoost(xdata, ydata, wt, 
#                   search = "default", 
#                   interaction = intr)
#   
#   pred = as.numeric(predict(xgfit, as.matrix(xdata)))
#   
#   xgbMetrics = getXgboostmetrics(xgfit, xdata, ydata, pred, wt)
#   
#   xgbMetrics = data.frame(
#     "model" = paste0("XGBd", intr),
#     "dependent" = y, 
#     "interaction" = intr, 
#     "transform" = "None",
#     xgbMetrics)
#   
#   allMetrics = rbind(allMetrics, xgbMetrics)
# }
# knitr::kable(allMetrics, row.names = F)

```

#### Using SOURCE_EUI as dependent variable

```{r, warning=FALSE}
library(doParallel)
ncore = 4
registerDoParallel(cores = ncore)
```

##### Using default search
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"
search = "default"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```

##### Using grid search
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"
search = "grid"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```


##### Using adaptive search
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"
search = "adaptive"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```


##### Using random search
```{r}
x = sourceEUI_attributes
y = "SOURCE_EUI"
w = "FINALWT"
search = "random"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

write.csv(allMetrics, 
          paste0(results_dir, building_type, ".csv"), 
          row.names = F)

allMetrics0 = allMetrics %>% filter(dependent == y)
knitr::kable(allMetrics0, row.names = F)

```


#### Using SOURCE_ENERGY as dependent variable


##### Using default search
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"
search = "default"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```


##### Using grid search
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"
search = "grid"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```


##### Using adaptive search
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"
search = "adaptive"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

knitr::kable(xgbMetrics, row.names = F)

```


##### Using random search
```{r}
x = sourceEnergy_attributes
y = "SOURCE_ENERGY"
w = "FINALWT"
search = "random"

xgbMetrics = XGBoost.predict(data, x, y, w, search)
allMetrics = rbind(allMetrics, xgbMetrics)

write.csv(allMetrics, 
          paste0(results_dir, building_type, ".csv"), 
          row.names = F)

allMetrics0 = allMetrics %>% filter(dependent == y)
knitr::kable(allMetrics0, row.names = F)

```




### Comparision of XGB models

```{r, warning=FALSE}
plotXgbR2 <- function(df, titl) {
  
  plot <- ggplot(df, aes(x = interaction, y=Adj.R.2, 
                          group=model, col=model)) + 
    geom_point(size=2) + geom_line(size=1) +  
    ggtitle(titl) + 
    theme_pubr(base_size=12) +
    theme(legend.position="top", legend.title = element_blank()) 

  return(plot)
}

plotXgbNRMSE <- function(df, titl) {
  
  df1 = melt(df, measure.vars = c("nrmse_iqr", "nrmse_mean", 
                                        "nrmse_sd"))
  df1$variable = toupper(df1$variable)
  plot <- ggplot(df1, aes(x = interaction, y=value, 
                          group=variable, col=variable)) + 
  geom_point(size=2) + geom_line(size=1) +
    facet_wrap(. ~ model, scales = "fixed", nrow=2) + 
    ggtitle(titl) + 
    theme_pubr(base_size=12) +
    theme(legend.position="top", legend.title = element_blank()) + 
    theme(strip.placement = "outside", strip.background = element_blank())
  
  return(plot)
}
```

#### XGB plots using Source EUI
```{r}
allMetrics0 = allMetrics %>%
  mutate(model = substr(model, 1, 4)) %>%
  filter(stringr::str_detect(model, "XGB")) %>%
  filter(dependent == "SOURCE_EUI")

plot1 = plotXgbR2(allMetrics0, "XGB models using source EUI")
plot2 = plotXgbNRMSE(allMetrics0, "XGB models using source EUI")

print(plot1)
print(plot2)

```

#### XGB plots using Source Energy
```{r}
allMetrics0 = allMetrics %>%
  mutate(model = substr(model, 1, 4)) %>%
  filter(stringr::str_detect(model, "XGB")) %>%
  filter(dependent == "SOURCE_ENERGY")

plot1 = plotXgbR2(allMetrics0, "XGB models using source energy")
plot2 = plotXgbNRMSE(allMetrics0, "XGB models using source energy")

print(plot1)
print(plot2)

```


### Comparision between MLR and XGB models

#### MLR and XGB plots using Source EUI
```{r}
allMetrics0 = allMetrics %>%
  mutate(model = substr(model, 1, 4)) %>%
  #filter(stringr::str_detect(model, "XGB")) %>%
  filter(dependent == "SOURCE_EUI")

plot1 = plotXgbR2(allMetrics0, "Comparison MLR and XGB models using source EUI")
plot2 = plotXgbNRMSE(allMetrics0, "Comparison MLR and XGB models using source EUI")

print(plot1)
print(plot2)

```

#### MLR and XGB plots using Source Energy
```{r}
allMetrics0 = allMetrics %>%
  mutate(model = substr(model, 1, 4)) %>%
  #filter(stringr::str_detect(model, "XGB")) %>%
  filter(dependent == "SOURCE_ENERGY")

plot1 = plotXgbR2(allMetrics0, "Comparison MLR and XGB models using source energy")
plot2 = plotXgbNRMSE(allMetrics0, "Comparison MLR and XGB models using source energy")

print(plot1)
print(plot2)

```
