---
title: "CBECS Warehouses - Data filteration"
author: "Pandarasamy Arjunan"
date: "3 June 2019"
output: 
  github_document:
    toc: true
#  html_document:
#    code_folding: "hide"
#    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(Metrics)
library(caret)
library(xgboost)
library(ggplot2)
library(reshape2)
library(ggpubr)
```


## Load dataset
```{r message=FALSE, warning=FALSE}
building_type = "warehouse"

filtered_dir = './data/cbecs/filtered/'
dir.create(filtered_dir, recursive = T, showWarnings = F)

features_dir = './data/cbecs/features/'
dir.create(features_dir, recursive = T, showWarnings = F)

results_dir = './results/cbecs/'
dir.create(results_dir, recursive = T, showWarnings = F)
```

```{r}
cbecs = read.csv("data/cbecs/2012_public_use_data_aug2016.csv")

var1 = c( 'SQFT', 'NFLOOR', 'NELVTR', 'NESLTR', 'COURT', 
          'MONUSE', 'OPNWE',  'WKHRS', 'NWKER', 'COOK', 
          'MANU', 'HEATP',  'COOLP',  'SNACK', 'FASTFD', 'CAF',
          'FDPREP', 'KITCHN', 'BREAKRM', 'OTFDRM', 'LABEQP', 'MCHEQP',
          'POOL', 'HTPOOL', 'RFGWIN', 'RFGOPN', 'RFGCLN', 'RFGVNN',
          'RFGICN', 'PCTERMN', 'LAPTPN', 'PRNTRN', 'SERVERN', 'TVVIDEON',
          'RGSTRN', 'COPIERN', 'HDD65','CDD65')

var2 = c( "PBAPLUS", "PBA", "FINALWT",
          "MFBTU", 
          "ELBTU", "NGBTU", "FKBTU", "DHBTU",
          "ONEACT", "ACT1", "ACT2", "ACT3", "ACT1PCT", "ACT2PCT", "ACT3PCT",
          "PRAMTC", "PRUNIT",
          "CWUSED", "WOUSED", "COUSED", "SOUSED", "PRUSED",
          "RFGSTP")

warehouses = cbecs[, c(var1, var2)]
```



## Apply filters

As per Energy Star's technical document [ENERGY STAR Score for Warehouses](https://www.energystar.gov/buildings/tools-and-resources/energy-star-score-warehouses), following filters are applied to define the peer group and to remove any outliers.

After applying each filter, the number of remaining buildings in the dataset (_Number Remaining: X_) and any difference (_Difference: X_) in count from the original Energy Star's technical documentation is also given. 

#. **Calculate source energy and source EUI**
    ```{r}
## convert electricity, natural gas, fuel oil, and district heat to source energy
w0 = warehouses %>% 
  mutate(ELBTU0 = ELBTU*2.80) %>%
  mutate(NGBTU0 = NGBTU*1.05) %>%
  mutate(FKBTU0 = FKBTU*1.01) %>%
  mutate(DHBTU0 = DHBTU*1.20) %>%
  mutate(SOURCE_ENERGY = rowSums(dplyr::select(., c(ELBTU0,NGBTU0,FKBTU0,DHBTU0)), na.rm = T)) %>% 
  mutate(SOURCE_EUI = round(SOURCE_ENERGY/SQFT, 2)) %>%
  mutate(SITE_EUI = round(MFBTU/SQFT, 2)) %>%
  mutate(NGBTU_PERCENT = round(NGBTU / SOURCE_ENERGY * 100, 2)) %>% 
  mutate(SUMBTU = rowSums(dplyr::select(., c(ELBTU,NGBTU,FKBTU,DHBTU)), na.rm = T))

#Is MFBTU the sum of ELBTU,NGBTU,FKBTU,DHBTU? YES.
#summary(o14$MFBTU - o14$SUMBTU)

    ```

#. **PBAPLUS = 9, 10, or 20**
Building Type Filter – CBECS defines building types according to the variable “PBAPLUS.” Distribution/Shipping Centers are coded as PBAPLUS=9; Non-Refrigerated Warehouses are coded as PBAPLUS=10; and Refrigerated Warehouses are coded as PBAPLUS=20.
<br/>Number Remaining: 678.
<br/>Difference: 0.
    ```{r}
w1 = w0 %>% filter(PBAPLUS %in% c(9, 10, 20))
    ```

#. **Must operate for at least 30 hours per week**
<br/>EPA Program Filter – Baseline condition for being a full time warehouse.
<br/>Number Remaining: 621.
<br/>Difference: 0.
    ```{r}    
    w2 = w1 %>% filter(WKHRS >= 30)
    ```

#. **Must have at least 1 worker**
<br/>EPA Program Filter – Baseline condition for being a full time warehouse
<br/>Number Remaining: 597.
<br/>Difference: 0.
    ```{r}
    w3 = w2 %>% filter(NWKER >= 1)
    ```

#. **Must operate for at least 10 months per year**
<br/>EPA Program Filter – Baseline condition for being a full time warehouse.
<br/>Number Remaining: 580.
<br/>Difference: 0.
    ```{r}
    w4 = w3 %>% filter(MONUSE >= 10)
    ```

#. **A single activity must characterize greater than 50% of the floor space**
<br/>EPA Program Filter – In order to be considered part of the warehouse peer group, more than 50% of the building must be defined as distribution/shipping center, non-refrigerated warehouse, or refrigerated warehouse.
<br/>Number Remaining: 568.
<br/>Difference: +25
    ```{r}
    w5 = w4 %>% 
      filter( (ONEACT == 1) |
                (ONEACT == 2 & 
                   ((ACT1 %in% c(13) & ACT1PCT > 50) | 
                    (ACT2 %in% c(13) & ACT2PCT > 50) | 
                    (ACT3 %in% c(13) & ACT3PCT > 50) )))

    # test code to verify the above filter
    # w51 = w4 %>% filter(ONEACT == 1)
    # w5a = w4 %>% filter(ONEACT == 2 & ACT1 == 13 & ACT1PCT > 50)
    # w5b = w4 %>% filter(ONEACT == 2 & ACT2 == 13 & ACT2PCT > 50)
    # w5c = w4 %>% filter(ONEACT == 2 & ACT3 == 13 & ACT3PCT > 50)
    # #select(c(ONEACT, ACT1, ACT2, ACT3, ACT1PCT, ACT2PCT, ACT3PCT)) %>% 
    # print(nrow(w51) + nrow(w5a) + nrow(w5b) + nrow(w5c))

    ```

#. **Must report energy usage**
<br/>EPA Program Filter – Baseline condition for being a full time warehouse.
<br/>Number Remaining: 562.
<br/>Difference: +19.
    ```{r}
    w6 = w5 %>% filter(!is.na(MFBTU))
    ```

#. **Must be less than or equal to 1,000,000 square feet**
<br/>Data Limitation Filter – CBECS masks surveyed properties above 1,000,000 square feet by applying regional averages.
<br/>Number Remaining: 555.
<br/>Difference: +19.
    ```{r}
    w7 = w6 %>% filter(SQFT <= 1000000)
    ```

#. **If propane is used, the amount category (PRAMTC) must equal 1, 2, or 3**
<br/>Data Limitation Filter – Cannot estimate propane use if the quantity is “greater than 1000” or unknown.
<br/>Number Remaining: 530.
<br/>Difference: +19.
    ```{r}
    w8 = w7 %>% filter(is.na(PRAMTC) | PRAMTC %in% c(1,2,3))
    ```

#. **If propane is used, the unit (PRUNIT) must be known**
<br/>Data Limitation Filter – Cannot estimate propane use if the unit is unknown.
<br/>Number Remaining: 526.
<br/>Difference: +19.
    ```{r}
    w9 = w8 %>% filter(is.na(PRUNIT) | PRUNIT %in% c(1,2))
    ```

#. **If propane is used, the maximum estimated propane amount must be 10% or less of the total source energy**
<br/>Data Limitation Filter – Because propane values are estimated from a range, propane is restricted to 10% of the total source energy.
<br/>Number Remaining: 510.
<br/>Difference: +6.
    ```{r}
    w10 = w9 %>% 
      filter(PRUSED == 2 | is.na(NGBTU_PERCENT) == T | 
            (PRUSED == 1 & NGBTU_PERCENT <= 10))

    ```

#. **Must not use chilled water, wood, coal, or solar**
<br/>Data Limitation Filter – CBECS does not collect quantities of chilled water, wood, coal, or solar.
<br/>Number Remaining: 499.
<br/>Difference: +6.
    ```{r}
    w11 = w10 %>% 
      filter(CWUSED == 2) %>%
      filter(WOUSED == 2) %>% 
      filter(COUSED == 2) %>% 
      filter(SOUSED == 2)
    ```

#. **Must have no more than 2.8 workers per 1,000 square feet**
<br/>Analytical Filter – Values determined to be statistical outliers.
<br/>Number Remaining: 487.
<br/>Difference: +4.
    ```{r}
    w12 = w11 %>% filter(NWKER  / SQFT * 1000 <= 2.8)
    ```
  

#. **Source EUI cannot be greater than 500 kBtu/ft2**
<br/>Analytical Filter – Values determined to be statistical outliers.
<br/>Number Remaining: 483.
<br/>Difference: +3.
    ```{r}
    w13 = w12 %>% filter(SOURCE_EUI <= 500)
    ```

#. **Percent Cooled plus Percent Cold Storage must be less than or equal to 100%**
<br/>Analytical Filter – Values exceed what is physically expected to be possible.
<br/>Number Remaining: 477.
<br/>Difference: +3.
    ```{r}
    w14 = w13 %>% 
      dplyr::mutate(COLD_SUM = 
                      rowSums(dplyr::select(., c(COOLP,RFGSTP)), na.rm = T)) %>%
      filter(COLD_SUM <= 100)
    ```

#. **Percent Heated plus Percent Cold Storage must be less than or equal to 100%**
<br/>Analytical Filter – Values exceed what is physically expected to be possible.
<br/>Number Remaining: 475.
<br/>Difference: +3.
    ```{r}
    w15 = w14 %>% 
      dplyr::mutate(HEAT_SUM = 
                      rowSums(dplyr::select(., c(HEATP,RFGSTP)), na.rm = T)) %>%
      filter(HEAT_SUM <= 100)
    ```


**Save the filtered dataset**
```{r}
write.csv(w15, paste0(filtered_dir, building_type, ".csv"), row.names = F)
```

## Prepare features

The final regression equation includes the following variables: 

 - Weekly Operating Hours
 - Number of Workers per 1,000 Square Feet
 - Percent Cold Storage
 - Heating Degree Days times Percent of the Building that is Heated
 - Cooling Degree Days times (Percent of the Building that is Cooled plus Percent Cold Storage)

```{r}
warehouse = read.csv(paste0(filtered_dir, building_type, ".csv"))

data = warehouse %>%
  mutate(NWKER_SQFT = NWKER/SQFT * 1000) %>%
  mutate(HDD65_HEATP = HDD65 * HEATP / 100) %>%
  mutate(CDD65_COLD_SUM = CDD65 * COLD_SUM / 100) %>%
  mutate_if(is.numeric, round, 3)

ivars = c(
  #"RFGSTP", ## too many missing values
  "COLD_SUM", 
  "SQFT", 
  "WKHRS", "NWKER_SQFT", 
  "HDD65_HEATP", "CDD65_COLD_SUM")

dvars  = c("SOURCE_EUI", "SOURCE_ENERGY", "FINALWT")

features = data[, c(ivars, dvars)]
#summary(features)
features = features %>% na.omit()

write.csv(features, 
          paste0(features_dir, building_type, ".csv"), 
          row.names = F)

```


## Descriptive statistics 
```{r include=FALSE}
library(knitr)
opts_chunk$set(results = 'asis',      
              comment = NA, 
              prompt = FALSE, 
              cache = FALSE)

library(summarytools)
st_options(plain.ascii = FALSE,       
            style = "rmarkdown",      
            footnote = NA,            
            subtitle.emphasis = FALSE)                                    
st_css()                              
```

```{r}
features1 = features
features1 = features1 %>% dplyr::select(-one_of('SOURCE_ENERGY', 'FINALWT'))

summarytools::descr(features1, stats = "common", 
                    transpose = TRUE, 
                    headings = FALSE)
```


```{r}
dfSummary(features1, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE)
```


**Extract R code from Rmd document**
```{r}
#knitr::purl("warehouse.Rmd", output = "warehouse.R", documentation = 2)
```


## Build predictive models

```{r}
source("models.R")
source("metrics.R")

data = read.csv(paste0(features_dir, building_type, ".csv"))

cat(colnames(data))

allMetrics = NULL

```


### Multiple Linear Regression (MLR)

#### Using SOURCE_EUI as dependent variable
```{r}
y = "SOURCE_EUI"
w = "FINALWT"
o = c("SOURCE_ENERGY", "SQFT")
x = setdiff(colnames(data), c(y, w, o))
wt = data[, w]
intr = 1

mlrFit = MLR(data, x, y, w, interaction = intr)

obs  = data[, y]
pred = as.numeric(predict(mlrFit))

mlrMetrics1 = getMLRmetrics(mlrFit, obs, pred, wt)
mlrMetrics1 = data.frame(
  "model" = "MLR",
  "dependent" = y,
  "interaction" = intr,
  "transform" = "meanCent",
  mlrMetrics1)

allMetrics = rbind(allMetrics, mlrMetrics1)

knitr::kable(mlrMetrics1, row.names = F)

```

#### Using SOURCE_ENERGY as dependent variable**
```{r}
y = "SOURCE_ENERGY"
w = "FINALWT"
o = c("SOURCE_EUI")
x = setdiff(colnames(data), c(y, w, o))
wt = data[, w]
intr = 1

mlrFit = MLR(data, x, y, w, interaction = intr)

obs  = data[, y]
pred = as.numeric(predict(mlrFit))

mlrMetrics2 = getMLRmetrics(mlrFit, obs, pred, wt)
mlrMetrics2 = data.frame(
  "model" = "MLR",
  "dependent" = y,
  "interaction" = intr,
  "transform" = "meanCent",
  mlrMetrics2)
allMetrics = rbind(allMetrics, mlrMetrics2)
knitr::kable(allMetrics, row.names = F)

```



### Multiple Linear Regression (MLR) with Interaction terms

#### Using SOURCE_EUI as dependent variable
```{r}
y = "SOURCE_EUI"
w = "FINALWT"
o = c("SOURCE_ENERGY", "SQFT")
x = setdiff(colnames(data), c(y, w, o))
wt = data[, w]

intr_depth = length(x)

for (intr in 2:intr_depth) {
  
  mlrFit = MLR(data, x, y, w, interaction = intr)
  obs  = data[, y]
  pred = as.numeric(predict(mlrFit))
  
  mlrMetrics = getMLRmetrics(mlrFit, obs, pred, wt)
  mlrMetrics = data.frame(
    "model" = paste0("MLRi", intr),
    "dependent" = y,
    "interaction" = intr,
    "transform" = "meanCent",
    mlrMetrics)
  
  allMetrics = rbind(allMetrics, mlrMetrics)
}

allMetrics0 = allMetrics %>% filter(dependent == y)
knitr::kable(allMetrics0, row.names = F)

```

#### Using SOURCE_ENERGY as dependent variable**
```{r}
y = "SOURCE_ENERGY"
w = "FINALWT"
o = c("SOURCE_EUI")
x = setdiff(colnames(data), c(y, w, o))
wt = data[, w]
intr_depth = length(x)

for (intr in 2:intr_depth) {
  
  mlrFit = MLR(data, x, y, w, interaction = intr)
  obs  = data[, y]
  pred = as.numeric(predict(mlrFit))
  
  mlrMetrics = getMLRmetrics(mlrFit, obs, pred, wt)
  mlrMetrics = data.frame(
    "model" = paste0("MLRi", intr),
    "dependent" = y,
    "interaction" = intr,
    "transform" = "meanCent",
    mlrMetrics)
  
  allMetrics = rbind(allMetrics, mlrMetrics)
}

write.csv(allMetrics, 
          paste0(results_dir, building_type, ".csv"), 
          row.names = F)

allMetrics0 = allMetrics %>% filter(dependent == y)
knitr::kable(allMetrics0, row.names = F)

```


### Comparision of MLR models

#### MLR plots using Source EUI
```{r, warning=FALSE}
mytheme = theme(legend.title = element_blank(),
           legend.text=element_text(size=12),
           axis.text=element_text(size=12),
           text=element_text(size=12))

plotR2 <- function(df, titl) {
  
  df1 = melt(df, measure.vars = c("R.2", "Adj.R.2"))
  
  plot <- ggplot(df1, aes(x = interaction, y=value, 
                          group=variable, col=variable)) + 
  geom_point(size=2) + geom_line(size=1) +
    ggtitle(titl) + 
    theme_pubr(base_size=12) +
    theme(legend.position="top", legend.title = element_blank())
  
  return(plot)
}

plotNRMSE <- function(df, titl) {
  
  df1 = melt(df, measure.vars = c("nrmse_iqr", "nrmse_mean", 
                                        "nrmse_sd"))
  df1$variable = toupper(df1$variable)
  
  plot <- ggplot(df1, aes(x = interaction, y=value, 
                          group=variable, col=variable)) + 
  geom_point(size=2) + geom_line(size=1) +
    ggtitle(titl) + 
    theme_pubr(base_size=12) +
    theme(legend.position="top", legend.title = element_blank())
    
  
  return(plot)
}  

```

```{r}

allMetrics0 = allMetrics %>%
  filter(stringr::str_detect(model, "MLR")) %>%
  filter(dependent == "SOURCE_EUI")

plot1 = plotR2(allMetrics0, "MLR models using source EUI")
plot2 = plotNRMSE(allMetrics0, "MLR models using source EUI")

print(plot1)
print(plot2)

```


#### MLR plots using Source Energy
```{r}

allMetrics0 = allMetrics %>%
  filter(stringr::str_detect(model, "MLR")) %>%
  filter(dependent == "SOURCE_ENERGY")

plot1 = plotR2(allMetrics0, "MLR models using source energy")
plot2 = plotNRMSE(allMetrics0, "MLR models using source energy")

print(plot1)
print(plot2)

```
