---
title: "CBECS Hotels - Data filteration"
author: "Pandarasamy Arjunan"
date: "3 June 2019"
output: 
  github_document:
    toc: true
#  html_document:
#    code_folding: "hide"
#    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load dataset
```{r message=FALSE, warning=FALSE}
library(dplyr)

save_dir1 = './data/filtered/'
dir.create(save_dir1, showWarnings = F)

save_dir2 = './data/features/'
dir.create(save_dir2, showWarnings = F)
```

```{r}
cbecs = read.csv("data/2012_public_use_data_aug2016.csv")

var1 = c( 'SQFT', 'NFLOOR', 'NELVTR', 'NESLTR', 'COURT', 
          'MONUSE', 'OPNWE',  'WKHRS', 'NWKER', 'COOK', 
          'MANU', 'HEATP',  'COOLP',  'SNACK', 'FASTFD', 'CAF',
          'FDPREP', 'KITCHN', 'BREAKRM', 'OTFDRM', 'LABEQP', 'MCHEQP',
          'POOL', 'HTPOOL', 'RFGWIN', 'RFGOPN', 'RFGCLN', 'RFGVNN',
          'RFGICN', 'PCTERMN', 'LAPTPN', 'PRNTRN', 'SERVERN', 'TVVIDEON',
          'RGSTRN', 'COPIERN', 'HDD65','CDD65')

var2 = c( "PBAPLUS", "PBA", "FINALWT",
          "MFBTU", 
          "ELBTU", "NGBTU", "FKBTU", "DHBTU",
          "ONEACT", "ACT1", "ACT2", "ACT3", "ACT1PCT", "ACT2PCT", "ACT3PCT",
          "PRAMTC", "PRUNIT",
          "CWUSED", "WOUSED", "COUSED", "SOUSED",  "PRUSED",
          "RFGSTP")

var3 = c( "RFGRSN", "RFGCOMPN", "RFGWIN", "RFGOPN", "RFGCLN", "RFGVNN")
var4 = c("LODGRM", "OCCUPYP", "LODOCCP")

hotels = cbecs[, c(var1, var2, var3, var4)]
```

## Apply filters

As per Energy Star's technical document [ENERGY STAR Score for Hotels](https://www.energystar.gov/buildings/tools-and-resources/energy-star-score-hotels), following filters are applied to define the peer group and to remove any outliers.

After applying each filter, the number of remaining buildings in the dataset (_Number Remaining: X_) and any difference (_Difference: X_) in count from the original Energy Star's technical documentation is also given. 

#. **Calculate source energy and source EUI**
    ```{r}
## convert electricity, natural gas, fuel oil, and district heat to source energy
h0 = hotels %>% 
  mutate(ELBTU0 = ELBTU*2.80) %>%
  mutate(NGBTU0 = NGBTU*1.05) %>%
  mutate(FKBTU0 = FKBTU*1.01) %>%
  mutate(DHBTU0 = DHBTU*1.20) %>%
  mutate(SOURCE_ENERGY = rowSums(dplyr::select(., c(ELBTU0,NGBTU0,FKBTU0,DHBTU0)), na.rm = T)) %>% 
  mutate(SOURCE_EUI = round(SOURCE_ENERGY/SQFT, 2)) %>%
  mutate(SITE_EUI = round(MFBTU/SQFT, 2)) %>%
  mutate(NGBTU_PERCENT = round(NGBTU / SOURCE_ENERGY * 100, 2)) %>% 
  mutate(SUMBTU = rowSums(dplyr::select(., c(ELBTU,NGBTU,FKBTU,DHBTU)), na.rm = T))

#Is MFBTU the sum of ELBTU,NGBTU,FKBTU,DHBTU? YES.
#summary(o14$MFBTU - o14$SUMBTU)

    ```

#. **PBAPLUS = 38 or 39**
<br/>Building Filter – CBECS defines building types according to the variable “PBAPLUS.” Hotels are coded as PBAPLUS = 38 and Motels/Inns are coded as PBAPLUS = 39.
<br/>Number Remaining: 220.
<br/>Difference: 0.
    ```{r}
    h1 = h0 %>% filter(PBAPLUS %in% c(38, 39))
    ```

#. **Must have at least 1 room**
<br/>EPA Program Filter – Baseline condition for being a full time hotel.
<br/>Number Remaining: 220.
<br/>Difference: 0.
    ```{r}
    h2 = h1 %>% filter( LODGRM >= 1)
    ```


#. **Must operate for 168 hours per week**
<br/>EPA Program Filter – Baseline condition for being a full time hotel.
<br/>Number Remaining: 218.
<br/>Difference: 0.
    ```{r}
    h3 = h2 %>% filter(WKHRS == 168)
    ```
    
    
#. **Must have at least 1 worker**
<br/>EPA Program Filter – Baseline condition for being a full time hotel.
<br/>Number Remaining: 215.
<br/>Difference: 0.
    ```{r}
    h4 = h3 %>% filter(NWKER >= 1)
    ```
    
    
#. **Must operate for at least 10 months per year**
<br/>EPA Program Filter – Baseline condition for being a functioning office building.
<br/>Number Remaining: 209.
<br/>Difference: 0.
    ```{r}
    h5 = h4 %>% filter(MONUSE >= 10)
    ```


#. **A single activity must characterize greater than 50% of the floor space**
<br/>EPA Program Filter – In order to be considered part of the hotel peer group, more than 50% of the building must be defined as a hotel.
<br/>This filter is applied by a set of screens. If the variable ONEACT=1, then one activity occupies 75% or more of the building. If the variable ONEACT=2, then the activities in the building are defined by ACT1, ACT2, and ACT3. One of these activities must be coded as lodging (PBAX=22), with a corresponding percent (ACT1PCT, ACT2PCT, ACT3PCT) that is greater than 50.
<br/>Number Remaining: 205.
<br/>Difference: +1.
    ```{r}
    h6 = h5 %>% 
      filter( (ONEACT == 1) |
            (ONEACT == 2 & 
               ((ACT1 %in% c(22) & ACT1PCT > 50) | 
                  (ACT2 %in% c(22) & ACT2PCT > 50) | 
                  (ACT3 %in% c(22) & ACT3PCT > 50) )))
    ```

#. **Must report energy usage**
<br/>EPA Program Filter – Baseline condition for being a functioning office building.
<br/>Number Remaining: 205.
<br/>Difference: +1.
    ```{r}
    h7 = h6 %>% filter(!is.na(MFBTU))
    ```


#. **Must be less than or equal to 1,000,000 square feet**
<br/>Data Limitation Filter – CBECS masks surveyed properties above 1,000,000 square feet by applying regional averages.
<br/>Number Remaining: 197.
<br/>Difference: +1.
    ```{r}
    h8 = h7 %>% filter(SQFT <= 1000000)
    ```

#. **If propane is used, the amount category (PRAMTC) must equal 1, 2, or 3**
<br/>Data Limitation Filter – Cannot estimate propane use if the quantity is “greater than 1000” or unknown.
<br/>Number Remaining: 186.
<br/>Difference: +1.
    ```{r}
    h9 = h8 %>% filter(is.na(PRAMTC) | PRAMTC %in% c(1,2,3))
    ```


#. **If propane is used, the unit (PRUNIT) must be known**
<br/>Data Limitation Filter – Cannot estimate propane use if the unit is unknown.
<br/>Number Remaining: 184.
<br/>Difference: +1.
    ```{r}
    h10 = h9 %>% filter(is.na(PRUNIT) | PRUNIT %in% c(1,2))
    ```


#. **If propane is used, the maximum estimated propane amount must be 10% or less of the total source energy**
<br/>Data Limitation Filter – Because propane values are estimated from a range, propane is restricted to 10% of the total source energy.
<br/>Number Remaining: 176.
<br/>Difference: -7.
    ```{r}
    h11 = h10 %>% 
      filter( PRUSED == 2 | is.na(NGBTU_PERCENT) == T | 
            ( PRUSED == 1 & NGBTU_PERCENT <= 10))
    ```


#. **must not use chilled water, wood, coal, or solar**
<br/>Data Limitation Filter – Because propane values are estimated from a range, propane is restricted to 10% of the total source energy.
<br/>Number Remaining: 171.
<br/>Difference: -6.
    ```{r}
    h12 = h11 %>% 
      filter(CWUSED == 2 & WOUSED == 2 & COUSED == 2 & SOUSED == 2)

    ```


#. **Must be at least 5,000 square feet**
<br/>Data Limitation Filter – Because propane values are estimated from a range, propane is restricted to 10% of the total source energy.
<br/>Number Remaining: 162.
<br/>Difference: -7.
    ```{r}
    h13 = h12 %>% filter(SQFT >= 5000)
    ```
    

#. **Must have Source EUI less than or equal to 400 kBtu/ft2**
<br/>Data Limitation Filter – Because propane values are estimated from a range, propane is restricted to 10% of the total source energy.
<br/>Number Remaining: 156.
<br/>Difference: -7.
    ```{r}
    h14 = h13 %>% filter(SOURCE_EUI <= 400)
    ```
    

#. **Must have no more than 4 rooms per 1,000 square feet**
<br/>Data Limitation Filter – Because propane values are estimated from a range, propane is restricted to 10% of the total source energy.
<br/>Number Remaining: 146.
<br/>Difference: -6.
    ```{r}
    h15 = h14 %>% filter(LODGRM/SQFT *1000 <= 4)
    ```
    
#. **Must have average occupancy greater than 40%**
<br/>Data Limitation Filter – Because propane values are estimated from a range, propane is restricted to 10% of the total source energy.
<br/>Number Remaining: 133.
<br/>Difference: -6.
    ```{r}
    h16 = h15 %>% filter(LODOCCP > 40)
    ```
    
**Save the filtered dataset**
```{r}
write.csv(h16, paste0(save_dir1, "hotel.csv"), row.names = F)
```


## Prepare features

The final regression equation includes the following variables:

 - Number of Guest Rooms per 1,000 Square Feet
 - Number of Workers per 1,000 Square Feet
 - Number of Commercial Refrigeration/Freezer Units (walk-in, open, and closed) per 1,000 Square Feet
 - Heating Degree Days times Percent of the Building that is Heated
 - Cooling Degree Days times Percent of the Building that is Cooled
 - Presence of a Commercial/Large Kitchen (1 = yes, 0 = no)

```{r}
save_dir1 = './data/filtered/'
save_dir2 = './data/features/'

hotel = read.csv(paste0(save_dir1, "hotel.csv"))

data = hotel %>%
  dplyr::mutate(LODGRM_SQFT = LODGRM/SQFT * 1000) %>%
  dplyr::mutate(NWKER_SQFT = NWKER/SQFT * 1000) %>%
  dplyr::mutate(RFG_TOT = rowSums(dplyr::select(., c(RFGRSN,RFGCOMPN,RFGWIN,RFGOPN,RFGCLN,RFGVNN)), na.rm = T)) %>% 
  dplyr::mutate(RFG_SQFT = RFG_TOT/SQFT * 1000) %>%
  dplyr::mutate(HDD65_HEATP = HDD65 * HEATP / 100) %>%
  dplyr::mutate(CDD65_COOLP = CDD65 * COOLP / 100) %>%
  dplyr::mutate(Kitchen = ifelse(FDPREP == 1, "Yes", "No")) %>%
  dplyr::mutate_if(is.numeric, round, 3)

ivars = c( "SQFT",
           "LODGRM_SQFT", "NWKER_SQFT", "RFG_SQFT",
          "HDD65_HEATP", "CDD65_COOLP", "Kitchen")

dvars  = c("SOURCE_EUI", "SOURCE_ENERGY", "FINALWT")

features = data[, c(ivars, dvars)]
#summary(features)

features = features %>% na.omit()
write.csv(features, paste0(save_dir2, "hotel.csv"), row.names = F)
```



## Descriptive statistics 
```{r include=FALSE}
library(knitr)
opts_chunk$set(results = 'asis',      
              comment = NA, 
              prompt = FALSE, 
              cache = FALSE)

library(summarytools)
st_options(plain.ascii = FALSE,       
            style = "rmarkdown",      
            footnote = NA,            
            subtitle.emphasis = FALSE)                                    
st_css()                              
```

```{r}
features1 = features

features1 = features1 %>% dplyr::select(-one_of('SOURCE_ENERGY', 'FINALWT'))

summarytools::descr(features1, stats = "common", 
                    transpose = TRUE, 
                    headings = FALSE)
```


```{r}
dfSummary(features1, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE)
```


**Extract R code from Rmd document**
```{r}
#knitr::purl("office.Rmd", output = "office.R", documentation = 2)
```

